### 2020-12-05 paper/main.tex
Work on paper

%
%  $Author: ienne $
%  $Date: 1995/09/15 15:20:59 $
%  $Revision: 1.4 $
%

% \documentclass[10pt,journal,cspaper,compsoc]{IEEEtran}   %%%tc version
\documentclass[10pt, conference]{IEEEtran}
%\documentclass[conference,compsoc]{IEEEtran}
%\documentclass[10pt, conference]{IEEEtran}
%\documentclass[times, 10pt,onecolumn]{article}
\usepackage{amsmath, amssymb, enumerate}
\usepackage{proof}

%%%%%%%%%%%%%%%% page control%%%%%%%%%%%%%%%%%
%\usepackage[margin=0.75in]{geometry}

%\linespread{0.991}  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% this is really useful
%\usepackage{cite}
\usepackage{fancybox}
\usepackage{amsfonts}
%\usepackage{algorithm}
%\usepackage[noend]{algorithmic}
\usepackage[usenames]{color}
%\usepackage{colortbl}
%\usepackage[ figure, boxed, vlined]{algorithm2e}
%\usepackage[linesnumbered,vlined]{algorithm2e}
%\usepackage[lined,boxed]{algorithm2e}
\usepackage{listings}

\usepackage[linesnumbered,vlined]{algorithm2e}
\usepackage{graphicx}
\usepackage{times}
\usepackage{psfrag}
\usepackage{subfigure}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{multirow}
%\usepackage{setspace}
%\usepackage{listings}
\usepackage{epsfig}
%\usepackage{epstopdf}
%\usepackage[font=small,labelfont=bf]{caption}
\usepackage{url}

\usepackage{color}
\def\fixme#1{\typeout{FIXED in page \thepage : {#1}}
%\bgroup \color{red}{} \egroup}
\bgroup \color{red}{[FIXME: {#1}]} \egroup}

%\usepackage[pdftex]{hyperref}
\usepackage{rotating,tabularx}

\interfootnotelinepenalty=10000

%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother

%\documentstyle[times,art10,twocolumn,latex8]{article}

%-------------------------------------------------------------------------
% take the % away on next line to produce the final camera-ready version
\pagestyle{plain}
%\thispagestyle{empty}
%\pagestyle{empty}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}

%% remaining budget share, used in task stall section.
\newcommand{\bottomrule}{\hline}
\newcommand{\toprule}{\hline}
\newcommand{\midrule}{\hline}
\newcommand{\ttt}{\texttt}
\newcommand{\rarr}{\rightarrow}
%-------------------------------------------------------------------------
\begin{document}

\title{A Domain Specific Language for SpectreGuard}
\author{David Young\\
d063y800@ku.edu\\
University of Kansas, USA\\
}

\maketitle
\thispagestyle{empty}
\begin{abstract}

Abstract goes here.

\end{abstract}

%-------------------------------------------------------------------------

\section{Introduction}
Introduction goes here.

\section{Background}
Cite a paper \cite{barroso2009datacenter}.

Cite multiple papers \cite{banga99resourcecontainers,barroso2009datacenter}

\section{Syntax}
...

\section{Sensitivity Types}
\begin{figure}[h]
  \centering
\resizebox{0.5\linewidth}{!}{
\begin{minipage}{\linewidth}
\begin{gather*}
  \infer{\ttt{$n$ :: Int}}{n \in \mathbb{N}}\\
  \infer{\ttt{Public :: Sensitivity}}{}\\
  \infer{\ttt{Secret :: Sensitivity}}{}\\
  \infer{\Gamma \vdash \ttt{x + y :: Int}}{%
    \Gamma \vdash \ttt{x :: Int}
    & \Gamma \vdash \ttt{y :: Int}}\\
  \infer{\Gamma \vdash \ttt{x <? y :: Expr $\sigma$ Bool}}{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ Int}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ Int}}\\
  \infer{\Gamma \vdash \ttt{a ! i :: Expr $\sigma$ $\tau$}}{%
    \Gamma \vdash \ttt{a :: Expr $\sigma$ (Ptr $\tau$)}
    & \Gamma \vdash \ttt{i :: Expr $\sigma$ Int}}\\
  \quad\infer{\Gamma \vdash \ttt{allocPublic @$\tau$ n :: Cmd (Expr Public (Ptr $\tau$))}}{\Gamma \vdash \ttt{n :: Int}}\\
  \quad\infer{\Gamma \vdash \ttt{allocSecret @$\tau$ n :: Cmd (Expr Secret (Ptr $\tau$))}}{\Gamma \vdash \ttt{n :: Int}}\\
  \infer{\Gamma \vdash \ttt{decl x :: Cmd (Expr Public $\tau$)}}{\Gamma \vdash \ttt{x :: $\tau$}}\\
  \infer{\Gamma \vdash \ttt{x .= y :: Cmd ()}}{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ $\tau$}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ $\tau$}}\\
  \infer{\Gamma \vdash \ttt{ifThenElse cond t f :: Cmd ()}}{%
    \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
    &\Gamma \vdash \ttt{t :: $\tau$}
    &\Gamma \vdash \ttt{f :: $\tau$}}\\
  \infer{\Gamma \vdash \ttt{while cond body :: Cmd ()}}{%
    \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
    & \Gamma \vdash \ttt{body :: Cmd $\tau$}}\\
  \infer{\Gamma \vdash \ttt{for init fn :: Cmd ()}}{%
    \Gamma \vdash \ttt{init :: Expr $\sigma$ $\tau$}
    & \Gamma \vdash \ttt{fn :: Expr $\sigma$ $\tau$ $\rarr$ (Expr $\sigma$ Bool, Cmd (), Cmd ())}
    }
\end{gather*}
\end{minipage}}
  \caption{Typing rules for sensitivity types}
\label{fig:SensTypes}
\end{figure}

...

\section{Information Flow Analysis}
...
\section{Examples}
...
% \section{Your System}
% ...
% \section{Evaluation}
% ...

\section{Future Work}

\section{Conclusion}
...
%-------------------------------------------------------------------------

\bibliographystyle{plain}
\bibliography{reference}
\end{document}

### 2020-12-05 proposal.tex
Work on paper

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage[]{biblatex}
\addbibresource{proposal.bib}

\date{}

\begin{document}

\hypertarget{project-proposal-a-language-for-securing-sensitive-data-against-spectre-attacks}{%
\section{Project Proposal: A Language for Securing Sensitive Data
Against Spectre
Attacks}\label{project-proposal-a-language-for-securing-sensitive-data-against-spectre-attacks}}

\hypertarget{david-young}{%
\subsection{David Young}\label{david-young}}

Spectre attacks are carried out by observing microarchitectural changes
that result from the speculative execution of instructions. The result
of such attacks is that memory can be leaked. This memory could include
sensitive information, such as passwords.

It is frequently the case that the programmer will know ahead of time
which variables will store particularly sensitive data, as is the case
with password-entry fields. \autocite{SpectreGuard}

Consider the following C program:

\bibliography{proposal}
\printbibliography

\end{document}

### 2020-12-05 src/Security/CodeGen/C.hs
memcpy

@@ -21,6 +21,8 @@ import           Control.Monad
 import           Control.Monad.Operational
 import           Data.List
 
+import           Debug.Trace
+
 genC :: forall a. Repr a => Cmd a -> CodeGen String
 genC = genCNamed <=< genNames
 
@@ -33,17 +35,19 @@ genC0 withSemi c =
     Return x -> return "" -- Commands cannot have values in this subset of C
 
     AllocSecret name size :>>= (k :: Expr s b -> _) -> do
-      let d = genDecl ctype name
-          alloc = "malloc(" <> show size <> " * sizeof(" <> ptrTypeRepr (ctype @b) <> "))"
+      let d = ptrTypeRepr (ctype @b) <> " " <> emitName name <> "[" <> show size <> "]"
+      -- let d = genDecl ctype name
+      --     alloc = "malloc(" <> show size <> " * sizeof(" <> ptrTypeRepr (ctype @b) <> "))"
       r <- genCNamed (mkCmd0 (k (Var name)))
 
-      return $ unlines'With r [stmt' withSemi [d, "=", alloc]]
+      return $ unlines'With r [stmt' withSemi [d]]
 
     AllocPublic name size :>>= (k :: Expr s b -> _) -> do
-      let d = genDecl ctype name
-          alloc = "malloc(" <> show size <> " * sizeof(" <> ptrTypeRepr (ctype @b) <> "))"
+      let d = ptrTypeRepr (ctype @b) <> " " <> emitName name <> "[" <> show size <> "]"
+      -- let d = genDecl ctype name
+      --     alloc = "malloc(" <> show size <> " * sizeof(" <> ptrTypeRepr (ctype @b) <> "))"
       r <- genCNamed (mkCmd0 (k (Var name)))
-      return $ unlines'With r [stmt' withSemi [d, "=", alloc]]
+      return $ unlines'With r [stmt' withSemi [d]]
 
     Decl name x :>>= k -> do
       let d = genDecl ctype name
@@ -55,14 +59,22 @@ genC0 withSemi c =
     Assign (Var n) e :>>= k -> do
       eCode <- genExprC e
       r <- genCNamed (mkCmd0 (k ()))
-      return $ unlines'With r [stmt' withSemi [emitName n, "=", eCode]]
+
+      case ctypeProxy n of
[…]

### 2020-12-05 src/Security/Repr.hs

@@ -5,6 +5,7 @@
 {-# LANGUAGE EmptyCase #-}
 {-# LANGUAGE DataKinds #-}
 {-# LANGUAGE KindSignatures #-}
+{-# LANGUAGE StandaloneDeriving #-}
 
 module Security.Repr where
 
@@ -21,10 +22,15 @@ data CType a where
   CBool :: CType Bool
   CPtr :: forall a. CType a -> CType (Ptr a)
 
+deriving instance Show (CType a)
+
 class Repr a where
   typeRepr :: CType a -> String
   ctype :: CType a
   lit :: a -> String
+
+ctypeProxy :: Repr a => proxy a -> CType a
+ctypeProxy _ = ctype
 
 ptrTypeRepr :: Repr a => CType (Ptr a) -> String
 ptrTypeRepr (CPtr ty) = typeRepr ty

### 2020-12-06 paper/main.tex
Work on information flow analysis rules

@@
 \usepackage{amsmath, amssymb, enumerate}
-\usepackage{proof}
+\usepackage{semantic}
 
@@
 \newcommand{\midrule}{\hline}
+
 \newcommand{\ttt}{\texttt}
 \newcommand{\rarr}{\rightarrow}
+\newcommand{\sarr}{\leadsto}
 %-------------------------------------------------------------------------
@@
 \section{Sensitivity Types}
+In Fig. \ref{fig:SensTypes}, it is assumed that $\tau$ and $\sigma$ are given by the
+following grammar:
+\begin{gather*}
+  \sigma ::= \ttt{Public}\;|\;\ttt{Secret}\\
+  \tau ::= \ttt{Int}\;|\;\ttt{Ptr}\;\tau\\
+  \alpha ::= \ttt{Cmd ()}\;|\;\ttt{Cmd (Expr $\sigma$ $\tau$)}
+\end{gather*}
+
 \begin{figure}[h]
   \centering
-\resizebox{0.5\linewidth}{!}{
+\resizebox{0.68\linewidth}{!}{
 \begin{minipage}{\linewidth}
+  \centering
 \begin{gather*}
-  \infer{\ttt{$n$ :: Int}}{n \in \mathbb{N}}\\
-  \infer{\ttt{Public :: Sensitivity}}{}\\
-  \infer{\ttt{Secret :: Sensitivity}}{}\\
-  \infer{\Gamma \vdash \ttt{x + y :: Int}}{%
+  \inference{}{\ttt{Public :: Sensitivity}}\\
+\\
+  \inference{}{\ttt{Secret :: Sensitivity}}\\
+\\
+  \inference{n \in \mathbb{N}}{\ttt{$n$ :: Int}}\\
+\\
+  \inference{%
     \Gamma \vdash \ttt{x :: Int}
-    & \Gamma \vdash \ttt{y :: Int}}\\
-  \infer{\Gamma \vdash \ttt{x <? y :: Expr $\sigma$ Bool}}{%
+    & \Gamma \vdash \ttt{y :: Int}}
+    {\Gamma \vdash \ttt{x + y :: Int}}\\
+  \\
+  \inference{%
     \Gamma \vdash \ttt{x :: Expr $\sigma$ Int}
-    & \Gamma \vdash \ttt{y :: Expr $\sigma$ Int}}\\
-  \infer{\Gamma \vdash \ttt{a ! i :: Expr $\sigma$ $\tau$}}{%
+    & \Gamma \vdash \ttt{y :: Expr $\sigma$ Int}}
+    {\Gamma \vdash \ttt{x <? y :: Expr $\sigma$ Bool}}\\
+  \\
+  \inference{%
     \Gamma \vdash \ttt{a :: Expr $\sigma$ (Ptr $\tau$)}
-    & \Gamma \vdash \ttt{i :: Expr $\sigma$ Int}}\\
-  \quad\infer{\Gamma \vdash \ttt{allocPublic @$\tau$ n :: Cmd (Expr Public (Ptr $\tau$))}}{\Gamma \vdash \ttt{n :: Int}}\\
-  \quad\infer{\Gamma \vdash \ttt{allocSecret @$\tau$ n :: Cmd (Expr Secret (Ptr $\tau$))}}{\Gamma \vdash \ttt{n :: Int}}\\
-  \infer{\Gamma \vdash \ttt{decl x :: Cmd (Expr Public $\tau$)}}{\Gamma \vdash \ttt{x :: $\tau$}}\\
-  \infer{\Gamma \vdash \ttt{x .= y :: Cmd ()}}{%
+    & \Gamma \vdash \ttt{i :: Expr $\sigma$ Int}}
+    {\Gamma \vdash \ttt{a ! i :: Expr $\sigma$ $\tau$}}\\
+  \\
+  \inference{\Gamma \vdash \ttt{n :: Int}}{\Gamma \vdash \ttt{allocPublic @$\tau$ n :: Cmd (Expr Public (Ptr $\tau$))}}\\
+\\
+  \inference{\Gamma \vdash \ttt{n :: Int}}{\Gamma \vdash \ttt{allocSecret @$\tau$ n :: Cmd (Expr Secret (Ptr $\tau$))}}\\
+\\
+  \inference{\Gamma \vdash \ttt{x :: $\tau$}}{\Gamma \vdash \ttt{decl x :: Cmd (Expr Public $\tau$)}}\\
+\\
+  \inference{%
     \Gamma \vdash \ttt{x :: Expr $\sigma$ $\tau$}
-    & \Gamma \vdash \ttt{y :: Expr $\sigma$ $\tau$}}\\
-  \infer{\Gamma \vdash \ttt{ifThenElse cond t f :: Cmd ()}}{%
+    & \Gamma \vdash \ttt{y :: Expr $\sigma$ $\tau$}}
+    {\Gamma \vdash \ttt{x .= y :: Cmd ()}}\\
+  \\
+  \inference{%
     \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
     &\Gamma \vdash \ttt{t :: $\tau$}
-    &\Gamma \vdash \ttt{f :: $\tau$}}\\
-  \infer{\Gamma \vdash \ttt{while cond body :: Cmd ()}}{%
+    &\Gamma \vdash \ttt{f :: $\tau$}}
+    {\Gamma \vdash \ttt{ifThenElse cond t f :: Cmd ()}}\\
+  \\
+  \inference{%
     \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
-    & \Gamma \vdash \ttt{body :: Cmd $\tau$}}\\
-  \infer{\Gamma \vdash \ttt{for init fn :: Cmd ()}}{%
-    \Gamma \vdash \ttt{init :: Expr $\sigma$ $\tau$}
-    & \Gamma \vdash \ttt{fn :: Expr $\sigma$ $\tau$ $\rarr$ (Expr $\sigma$ Bool, Cmd (), Cmd ())}
-    }
+    & \Gamma \vdash \ttt{body :: Cmd $\alpha$}}
+    {\Gamma \vdash \ttt{while cond body :: Cmd ()}}\\
+  \\
+  \inference{%
+    \Gamma \vdash \ttt{init :: Expr $\sigma$ $\tau$}\\
+    \Gamma \vdash \ttt{fn :: Expr $\sigma$ $\tau$ $\rarr$ (Expr $\sigma$ Bool, Cmd (), Cmd ())}
+    }{\Gamma \vdash \ttt{for init fn :: Cmd ()}}
 \end{gather*}
@@
 \section{Information Flow Analysis}
+\begin{figure}[h]
+  \centering
+\resizebox{0.68\linewidth}{!}{
+\begin{minipage}{\linewidth}
+  \centering
+\begin{gather*}
+  \inference{%
+    \Delta;\Gamma \vdash \ttt{x :: $\tau$}
+    \\ \Delta;\Gamma \vdash \ttt{k :: Expr Public $\tau$ $\rarr$ Cmd $\alpha$}
+    \\ \Delta;\Gamma\vdash A(\ttt{decl v >>= ($\lambda$x $\rarr$ k)})
+    }
+    {%
+      \Delta,Pub(x);\Gamma \vdash A(\ttt{k})
+    }\\
+    \\
+  \inference{%
+    \Delta;\Gamma \vdash \ttt{x :: Expr Public $\tau$}
+    & \Delta;\Gamma \vdash \ttt{y :: Expr Public $\tau$}
+    \\ \Delta;\Gamma \vdash \ttt{k :: () $\rarr$ Cmd $\alpha$}
+    & \Delta;\Gamma \vdash A(\ttt{(x .= y) >>= k})
+    \\ \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
+    }
+    {%
+      \Delta;\Gamma \vdash \ttt{x} \sarr L(\ttt{x})
+    }\\
+  \\
+  \inference{%
+    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
+    & \Delta;\Gamma \vdash \ttt{body :: Cmd $\alpha$}
+    \\ \Delta;\Gamma \vdash A(\ttt{while cond body})
+    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
+    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
+    }
+    {%
+      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{body})
+    }\\
+  \\
+  \inference{%
+    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
+    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
+    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
+    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
+    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
+    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
+    }
+    {%
+      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{t})
+    }\\
+  \\
+  \inference{%
+    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
+    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
+    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
+    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
+    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
+    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
+    }
+    {%
+      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{f})
+    }\\
+  \\
+  \inference{%
+    \Delta;\Gamma \vdash v \in L(\ttt{x})
+    }
+    {%
+      \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
+    }
+\end{gather*}
+\end{minipage}}
+  \caption{Information flow analysis rules which define the relation $\sarr$}
+\label{fig:FlowRules}
+\end{figure}
 ...

### 2020-12-06 src/Security/CodeGen/C.hs
generate SpectreGuard annotation properly for arrays

@@ -35,22 +35,19 @@ genC0 withSemi c =
     Return x -> return "" -- Commands cannot have values in this subset of C
 
     AllocSecret name size :>>= (k :: Expr s b -> _) -> do
-      let d = ptrTypeRepr (ctype @b) <> " " <> emitName name <> "[" <> show size <> "]"
-      -- let d = genDecl ctype name
-      --     alloc = "malloc(" <> show size <> " * sizeof(" <> ptrTypeRepr (ctype @b) <> "))"
+      let d = genDecl (Just size) ctype name
       r <- genCNamed (mkCmd0 (k (Var name)))
 
       return $ unlines'With r [stmt' withSemi [d]]
 
     AllocPublic name size :>>= (k :: Expr s b -> _) -> do
-      let d = ptrTypeRepr (ctype @b) <> " " <> emitName name <> "[" <> show size <> "]"
-      -- let d = genDecl ctype name
-      --     alloc = "malloc(" <> show size <> " * sizeof(" <> ptrTypeRepr (ctype @b) <> "))"
+      -- let d = ptrTypeRepr (ctype @b) <> " " <> emitName name <> "[" <> show size <> "]"
+      let d = genDecl (Just size) ctype name
       r <- genCNamed (mkCmd0 (k (Var name)))
       return $ unlines'With r [stmt' withSemi [d]]
 
     Decl name x :>>= k -> do
-      let d = genDecl ctype name
+      let d = genDecl Nothing ctype name
           vName = Var name
       xCode <- genExprC (Literal @Public x)
       r <- genCNamed (mkCmd0 (k vName))
@@ -117,7 +114,7 @@ genC0 withSemi c =
       r <- genCNamed (mkCmd0 (k ()))
 
       return $ unlines'With r
-        ["for (" ++ genDecl ctype loopVar ++ " = " ++ initCode ++ "; " ++ condCode ++ "; " ++ updateCode ++ ") {"
+        ["for (" ++ genDecl Nothing ctype loopVar ++ " = " ++ initCode ++ "; " ++ condCode ++ "; " ++ updateCode ++ ") {"
         ,block bodyCode
         ,"}"
         ]

### 2020-12-06 src/Security/Repr.hs

@@ -56,13 +56,16 @@ instance Repr () where
 
 instance Repr a => Repr (Name s a) where
 
-genDecl :: forall (s :: Sensitivity) a. (Repr a) => CType a -> Name s a -> String
-genDecl ty n =
+genDecl :: forall (s :: Sensitivity) a. (Repr a) => Maybe Int -> CType a -> Name s a -> String
+genDecl sizeMaybe ty n =
   case nameSens n of
     PublicSing -> leftPart
     SecretSing -> unwords [leftPart, "__attribute__((nospec))__"]
   where
-    leftPart = unwords [typeRepr ty, emitName n]
+    leftPart =
+      case sizeMaybe of
+        Just size -> unwords [typeRepr ty, emitName n <> "[" <> show size <> "]"]
+        _ -> unwords [typeRepr ty, emitName n]
 
 
   -- case sing :: Sing s of

### 2020-12-06 paper/main.tex
Abstract and syntax

@@
 \usepackage{semantic}
+\usepackage{soul}
+\usepackage{listings}
 
@@
 
+\lstset{breaklines=true, basicstyle=\ttfamily\tiny, escapeinside={(*@}{@*)}}
+
 %\usepackage[pdftex]{hyperref}
@@
 
+\setlength\extrarowheight{1.5pt}
+
 \newcommand{\ttt}{\texttt}
@@
 
-Abstract goes here.
+  A Spectre mitigation strategy in the form of a mechanism for marking variables as "non-speculative" was developed in
+  \cite{SpectreGuard}. In this paper, we develop an embedded domain specific language (EDSL) in Haskell to provide
+  support for this feature. The static type system of Haskell is used so that many basic forms of copying
+  secret variables to public variables are disallowed. Additionally, a static analysis was developed which
+  will detect some cases of secret variables leaking to public variables via control flow constructs.
 
@@
 \section{Background}
-Cite a paper \cite{barroso2009datacenter}.
+Cite a paper. % \cite{barroso2009datacenter}.
 
-Cite multiple papers \cite{banga99resourcecontainers,barroso2009datacenter}
+Cite multiple papers. % \cite{banga99resourcecontainers,barroso2009datacenter}
 
 \section{Syntax}
-...
+A correspondence between the syntax of the EDSL, which is inherited from
+Haskell, and the C language is given in Fig. \ref{fig:Syntax}. In the right column, an
+overline indicates that the transformation from EDSL to C is recursively
+performed to the expression or command underneath the overline.
+
+\begin{figure}[h]
+\begin{tabular}{|l|l|}
+  \hline
+  EDSL syntax & C syntax \\
+  \hline
+  \begin{lstlisting}
+  v <- decl x
+  \end{lstlisting}
+  & \begin{lstlisting}
+  int v = x;
+  \end{lstlisting}\\
+
+  \hline
+  \begin{lstlisting}
+  v <- allocPublic @Int n
+  \end{lstlisting}
+  & \begin{lstlisting}
+  int v[n];
+  \end{lstlisting}\\
+
+  \hline
+  \begin{lstlisting}
+  v <- allocPrivate @Int n
+  \end{lstlisting}
+  & \begin{lstlisting}
+  int v[n] __attribute__((__nospec__));
+  \end{lstlisting}\\
+
+  \hline
+  \begin{lstlisting}
+  arrA .= arrB
+  \end{lstlisting}
+  & \begin{lstlisting}
+  memcpy(arrA, arrB, sizeof(arrA));
+  \end{lstlisting}\\
+
+  \hline
+  \begin{lstlisting}
+  i .= j
+  \end{lstlisting}
+  & \begin{lstlisting}
+  i = j;
+  \end{lstlisting}\\
+
+  \hline
+  \begin{lstlisting}
+  arr ! i
+  \end{lstlisting}
+  & \begin{lstlisting}
+  arr[i]
+  \end{lstlisting}\\
+
+  \hline
+  \begin{lstlisting}
+  x <? y
+  \end{lstlisting}
+  & \begin{lstlisting}
+  x < y
+  \end{lstlisting}\\
+
+  \hline
+  \begin{lstlisting}
+  while cond body
+  \end{lstlisting}
+  & \begin{lstlisting}
+  while ((*@$\overline{\ttt{cond}}$@*)) { (*@$\overline{\ttt{body}}$@*) }
+  \end{lstlisting}\\
+
+  \hline
+  \begin{lstlisting}
+  if cond t f
+  \end{lstlisting}
+  & \begin{lstlisting}
+  if ((*@$\overline{\ttt{cond}}$@*)) { (*@$\overline{\ttt{t}}$@*) } else { (*@$\overline{\ttt{t}}$@*) }
+  \end{lstlisting}\\
+
+  \hline
+  \begin{lstlisting}
+  for init (\i -> (cond, update, body))
+  \end{lstlisting}
+  & \begin{lstlisting}
+  for (int i = (*@$\overline{\ttt{init}}$@*); (*@$\overline{\ttt{cond}}$@*); (*@$\overline{\ttt{update}}$@*))
+    { (*@$\overline{\ttt{body}}$@*) }
+  \end{lstlisting}\\
+
+  \hline
+\end{tabular}
+\caption{Syntax of the EDSL vs C syntax}
+\label{fig:Syntax}
+\end{figure}
 
@@
 \end{gather*}
+
+A typing judgement is expressed with the syntax
+
+\begin{equation*}
+  \ttt{x :: $\beta$}
+\end{equation*}
+
+where \ttt{x} is some expression or command in the EDSL. This judgment means
+that \ttt{x} has type $\beta$. This is the same syntax used by Haskell, and by extension
+the EDSL, to explicitly specify a type in an expression.
 

### 2020-12-06 paper/main.tex
Some description of the types and future work

@@
 \section{Sensitivity Types}
+The Haskell type system is leveraged to perform a basic static consistency check of the sensitivities
+of variables, so that a variable does not get assigned to a variable of a different sensitivity. The
+logical inference rules corresponding to this check are given in Fig. \ref{fig:SensTypes}.
+
 In Fig. \ref{fig:SensTypes}, it is assumed that $\tau$ and $\sigma$ are given by the
@@
 \section{Future Work}
+A further investigation into the tradeoffs and possible additional features of
+the information flow analysis is likely to be useful. This could provide a more
+accurate and succinct picture to programmers of where leaks are occurring, or
+potentially occurring.
+
+Additionally, features to safely convert between sensitivity levels could prove
+useful. A conversion from public to secret would be straightforward. A conversion
+going the other direction could be provided by an instruction in the EDSL
+which might perform a mitigation measure, such as a cache flush. \cite{PLtea-james}
 

### 2020-12-06 paper/main.tex
an inference reference; change size of syntax table

@@
 
-\lstset{breaklines=true, basicstyle=\ttfamily\tiny, escapeinside={(*@}{@*)}}
+\lstset{breaklines=true, basicstyle=\ttfamily\fontsize{6}{7}\selectfont, escapeinside={(*@}{@*)}}
 
@@
 \setlength\extrarowheight{1.5pt}
+\setlength{\tabcolsep}{1pt}
 
@@
 
-  A Spectre mitigation strategy in the form of a mechanism for marking variables as "non-speculative" was developed in
-  \cite{SpectreGuard}. In this paper, we develop an embedded domain specific language (EDSL) in Haskell to provide
-  support for this feature. The static type system of Haskell is used so that many basic forms of copying
-  secret variables to public variables are disallowed. Additionally, a static analysis was developed which
-  will detect some cases of secret variables leaking to public variables via control flow constructs.
+  A Spectre mitigation strategy in the form of a mechanism for marking variables
+  as "non-speculative" was developed in \cite{SpectreGuard}. In this paper, we
+  develop an embedded domain specific language (EDSL) in Haskell to provide
+  support for this feature, with a backend that generates C code. The static
+  type system of Haskell is used so that many basic forms of copying secret
+  variables to public variables are disallowed. Additionally, a static analysis
+  was developed which will detect some cases of secret variables leaking to
+  public variables via control flow constructs.
 
@@
 performed to the expression or command underneath the overline.
+
+This also outlines procedure that the C code generator uses.
 
@@
   \begin{lstlisting}
-  for init (\i -> (cond, update, body))
+  for init
+    (\i ->
+      (cond, update, body))
   \end{lstlisting}
@@
 of variables, so that a variable does not get assigned to a variable of a different sensitivity. The
-logical inference rules corresponding to this check are given in Fig. \ref{fig:SensTypes}.
+logical inference rules corresponding to this check are given in Fig. \ref{fig:SensTypes}. An introduction
+to this style of inference rule system, with many examples and applications in the study of programming languages, is given in \cite{HarperFoundations}.
 
@@
 
-where \ttt{x} is some expression or command in the EDSL. This judgment means
-that \ttt{x} has type $\beta$. This is the same syntax used by Haskell, and by extension
-the EDSL, to explicitly specify a type in an expression.
+where \ttt{x} is some expression or command in the EDSL. This judgement means
+that \ttt{x} has type $\beta$. This is also the same syntax used by Haskell, and by extension
+the EDSL, to explicitly specify the type of any expression when necessary or desired.
 
@@
 Additionally, features to safely convert between sensitivity levels could prove
-useful. A conversion from public to secret would be straightforward. A conversion
+useful. A conversion from public to secret would be straightforward. A situational conversion
 going the other direction could be provided by an instruction in the EDSL
-which might perform a mitigation measure, such as a cache flush. \cite{PLtea-james}
+which might perform a Spectre mitigation measure, such as a cache flush. \cite{PLtea-james}
 

### 2020-12-06 paper/main.tex
More description of type-level stuff, additional related citations

@@
 %\usepackage[font=small,labelfont=bf]{caption}
-\usepackage{url}
+% \usepackage{url}
+\usepackage[hyphens]{url}
 
@@
   & \begin{lstlisting}
-  if ((*@$\overline{\ttt{cond}}$@*)) { (*@$\overline{\ttt{t}}$@*) } else { (*@$\overline{\ttt{t}}$@*) }
+  if ((*@$\overline{\ttt{cond}}$@*)) { (*@$\overline{\ttt{t}}$@*) } else { (*@$\overline{\ttt{f}}$@*) }
   \end{lstlisting}\\
@@
 The Haskell type system is leveraged to perform a basic static consistency check of the sensitivities
-of variables, so that a variable does not get assigned to a variable of a different sensitivity. The
+of variables, so that a variable does not get assigned to a variable of a different sensitivity. This
+is done by making the \verb|Expr| type constructor take a phantom type argument~\cite{Phantom}. The
 logical inference rules corresponding to this check are given in Fig. \ref{fig:SensTypes}. An introduction
 to this style of inference rule system, with many examples and applications in the study of programming languages, is given in \cite{HarperFoundations}.
+
+Singletons~\cite{SingletonsPaper} are used to preserve this type level at runtime, so that the
+code generator can generate SpectreGuard annotations where appropriate.
 
@@
 accurate and succinct picture to programmers of where leaks are occurring, or
-potentially occurring.
+potentially occurring. It is possible that some of these other leak conditions
+could be incorporated into the type system, by exploiting the dependent type
+features enabled by singletons~\cite{SingletonsPaper} and, in the future, by Dependent Haskell.~\cite{DepHaskSpec}
+Dependent types provide a powerful technique for writing programs at a type-level, which
+will be executed at compile-time by the type checker.~\cite{CertProg}
 

### 2020-12-06 paper/main.tex
bind typing rule
improved natural number typing rule
improved addition typing rule

@@
 \\
-  \inference{n \in \mathbb{N}}{\ttt{$n$ :: Int}}\\
+  \inference{n \in \mathbb{N}}{\ttt{$n$ :: Expr $\sigma$ Int}}\\
 \\
   \inference{%
-    \Gamma \vdash \ttt{x :: Int}
-    & \Gamma \vdash \ttt{y :: Int}}
-    {\Gamma \vdash \ttt{x + y :: Int}}\\
+    \Gamma \vdash \ttt{x :: Expr $\sigma$ Int}
+    & \Gamma \vdash \ttt{y :: Expr $\sigma$ Int}}
+    {\Gamma \vdash \ttt{x + y :: Expr $\sigma$ Int}}\\
   \\
@@
     \Gamma \vdash \ttt{fn :: Expr $\sigma$ $\tau$ $\rarr$ (Expr $\sigma$ Bool, Cmd (), Cmd ())}
-    }{\Gamma \vdash \ttt{for init fn :: Cmd ()}}
+    }{\Gamma \vdash \ttt{for init fn :: Cmd ()}}\\
+  \\
+  \inference{%
+    \Gamma \vdash \ttt{c :: Cmd (Expr $\sigma$ $\tau$)}
+    & \ttt{x} \notin dom(\Gamma)
+    \\ \Gamma \vdash \ttt{($\lambda$ x $\rarr$ body) :: Expr $\sigma$ $\tau$ $\rarr$ Cmd $\alpha$}
+  }{%
+    \Gamma \vdash \ttt{(\textbf{do} \{ x <- c; body \}) :: Cmd $\alpha$}
+  }
 \end{gather*}

### 2020-12-06 paper/main.tex
Included other Int literal typing rule
Some examples in paper

@@
 \\
+  \inference{n \in \mathbb{N}}{\ttt{$n$ :: Int}}\\
+  \\
   \inference{n \in \mathbb{N}}{\ttt{$n$ :: Expr $\sigma$ Int}}\\
@@
 ...
+
+\section{Examples}
+
+A couple of simple examples illustrate the basic typing rules:
+
+\begin{lstlisting}[language=haskell]
+example1 :: Cmd ()
+example1 = do
+  array1 <- allocSecret @Int 8
+  array2 <- allocSecret @Int 8
+
+  array2 .= array1
+\end{lstlisting}
+
+\noindent This first example passes the type checker with no problem: the array copy
+is being performed from one secret array to another secret array.
+
+The next example does not type check:
+
+\begin{lstlisting}[language=haskell]
+  -- This example fails to type check
+example2 :: Cmd ()
+example2 = do
+  array1 <- allocSecret @Int 8
+  array2 <- allocPublic @Int 8
+  (*@\color{red}array2 .= array1@*)
+\end{lstlisting}
+
+\noindent \ttt{example2} fails to type check since \ttt{array1} and \ttt{array2} have
+different sensitivity annotations, while the type of the \ttt{(.=)} operation
+requires that both arguments have the same sensitivity annotation. This restriction can
+be seen in the typing rule for \ttt{(.=)} in Fig. \ref{fig:SensTypes}.
+
+Turning to more complex examples, we can see that the following example type checks
+
+\begin{lstlisting}
+example3 :: Cmd ()
+example3 = do
+  arrayA <- allocSecret @Int 8
+  arrayB <- allocSecret @Int 8
+
+  for (0 :: Expr Secret Int) (\i -> ((i <? 8), (i += 1), do
+    (arrayA ! i) .= (arrayB ! i)))
+\end{lstlisting}
+
+\noindent This demonstrates a basic \ttt{for} loop and the array indexing syntax. Again, the
+only copies happen between two variables with the same sensitivity level, so this
+program is well-typed.
+
+The next slightly more complex example exhibits a limitation of this sensitivity type checking
+
+\begin{lstlisting}
+example4 :: Cmd ()
+example4 = do
+  secretArray <- allocSecret @Int 8
+  publicArray <- allocPublic @Int 8
+
+  for (0 :: Expr Public Int) (\i -> ((i <? 8), (i += 1), do
+    leak <- decl (0 :: Int)
+    for (0 :: Expr Secret Int) (\j -> ((j <? (secretArray ! i))
+                                      ,(j += 1)
+                                      ,do
+      leak += 1))
+    (publicArray ! i) .= leak))
+\end{lstlisting}
+
+In this code, the entire contents of the secret variable \ttt{secretArray} is leaked
+to the public variable \ttt{publicArray}, despite the two variables having different
+sensitivity annotations and therefore type checking without error. This is the
+result of information being indirectly leaked from the secret variable to the
+public variable via a control flow construct: in this case, the innermost \ttt{for} loop.
 
@@
 ...
-\section{Examples}
-...
+
 % \section{Your System}

### 2020-12-06 paper/main.tex
Lead in to analysis section

@@
 
-In this code, the entire contents of the secret variable \ttt{secretArray} is leaked
-to the public variable \ttt{publicArray}, despite the two variables having different
-sensitivity annotations and therefore type checking without error. This is the
+Even though this code type checks without error, the entire contents of the secret variable \ttt{secretArray} is leaked
+to the public variable \ttt{publicArray}. The leak occurs despite the fact that the two variables have different
+sensitivity annotations. This is the
 result of information being indirectly leaked from the secret variable to the
@@
 
+This kind of leak directly motivates the analysis in Section \ref{sec:Analysis}. This analysis will perform
+some level of checking beyond the relatively basic sensitivity type check described so far.
+
 \section{Information Flow Analysis}
+\label{sec:Analysis}
 \begin{figure}[h]

### 2020-12-06 paper/main.tex
wibble

@@
 
-The next slightly more complex example exhibits a limitation of this sensitivity type checking
+The next slightly more complex example exhibits an important limitation of this sensitivity type checking:
 
@@
 
-Even though this code type checks without error, the entire contents of the secret variable \ttt{secretArray} is leaked
+\noindent Even though this code type checks without error, the entire contents of the secret variable \ttt{secretArray} is leaked
 to the public variable \ttt{publicArray}. The leak occurs despite the fact that the two variables have different

### 2020-12-06 src/Security/CodeGen/Types.hs
More succinct generated names

@@ -64,12 +64,12 @@ newUniq = do
 newNameWith :: forall s a. SingI s => String -> CodeGen (Name s a)
 newNameWith readableStr = do
   uniq <- newUniq
-  return (Name sing ("_sec_" <> readableStr <> "_" <> show uniq))
+  return (Name sing ("_s_" <> readableStr <> "_" <> show uniq))
 
 freshName :: forall s a. SingI s => CodeGen (Name s a)
 freshName = do
   uniq <- newUniq
-  return (Name sing ("_fresh_sec_" <> show uniq))
+  return (Name sing ("_fs_" <> show uniq))
 
 emitName :: forall s a. Name s a -> String
 emitName (Name _ n) = n

### 2020-12-06 paper/main.tex
Analysis section and more complex example

@@
 \section{Examples}
+\label{sec:Examples}
 
@@
 \label{sec:Analysis}
+
+In Section \ref{sec:Examples}, a significant limitation of the sensitivity type checking
+was outlined. In this section we address this limitation using a static analysis technique.
+Possible leaks from secret variables to public variables via control flow constructs will
+be analyzed and the results of this analysis will be described in the form of
+a forest of trees, given in DOT format (which can then be converted to other formats,
+such as PDF)~\cite{DOT}. The C code generated from \ttt{example4} is shown in Fig. \ref{fig:GenC4}.
+Note that the secret array is named \verb|_fs_0| and the public array is named \verb|_fs_1| by the
+code generator. From the original \ttt{example4}, the information flow analyzer generates the
+graph given in Fig. \ref{fig:Analysis4}. Secret variables are represented as nodes with
+a rectangular shape and public variables are represented as nodes with an elliptic shape. An
+arrow going from one node to another represents a possible information leak from the first
+node to the second node due to a control flow construct.
+
+\begin{figure}[h]
+\begin{lstlisting}{language=C}
+int* _fs_0[8] __attribute__((nospec))__;
+int* _fs_1[8];
+for (int _fs_2 = 0; _fs_2 < 8; _fs_2 = _fs_2 + 1) {
+  int _fs_3 = 0;
+  for (int _fs_4 __attribute__((nospec))__ = 0;
+       _fs_4 < (_fs_0[_fs_2]);
+       _fs_4 = _fs_4 + 1) {
+    _fs_3 = _fs_3 + 1;
+  }
+  _fs_1[_fs_2] = _fs_3;
+}
+\end{lstlisting}
+\caption{C code generated from \ttt{example4}}
+\label{fig:GenC4}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+  \resizebox{0.3\columnwidth}{4cm}{\includegraphics{Diagrams/example4-analysis.pdf}}
+\caption{Results of leak analysis on \ttt{example4}}
+\label{fig:Analysis4}
+\end{figure}
+
+A more complicated example is \ttt{example6} in the following:
+
+\begin{lstlisting}[language=Haskell]
+example5 :: Cmd ()
+example5 = do
+  secretArray <- allocSecret @Int 8
+  publicArray <- allocPublic @Int 8
+
+  for (0 :: Expr Public Int) (\i -> ((i <? 8), (i += 1), do
+
+    leak <- decl (0 :: Int)
+
+    for (0 :: Expr Secret Int) (\j -> ((j <? (secretArray ! i))
+                                      ,(j += 1)
+                                      ,do
+      leak += 1
+      ))
+    (publicArray ! i) .= leak
+    ))
+
+  secretArrayA <- allocSecret @Int 8
+  secretArrayB <- allocSecret @Int 8
+  publicArray2 <- allocPublic @Int 8
+
+  secretArrayA .= secretArray
+  secretArrayB .= secretArrayA
+
+  for (0 :: Expr Public Int) (\i -> ((i <? 8), (i += 1), do
+
+    leak2 <- decl (0 :: Int)
+
+    for (0 :: Expr Secret Int) (\j -> ((j <? (secretArrayB ! i))
+                                      ,(j += 1)
+                                      ,do
+      leak2 += 1
+      ))
+    (publicArray2 ! i) .= leak2
+    ))
+\end{lstlisting}
+
+In the generated code for \ttt{example5}, we have the correspondence between variables in the EDSL code and the
+generated C code given in the table in TABLE \ref{table:Names5}. As both the C code generator and the
+static analysis tool use the same name generator, these names stay stable across the results of both. The analysis of \ttt{example5} is given in Fig. \ref{fig:Analysis5}.
+
+\begin{table}[h]
+  \centering
+  \begin{tabular}{|c|c|}
+    \hline
+    EDSL name & Generated C Name \\
+    \hline
+    \verb|secretArray| & \verb|_fs_0|\\
+    \verb|publicArray| & \verb|_fs_1|\\
+    \verb|leak| & \verb|_fs_3|\\
+    \verb|secretArrayA| & \verb|_fs_5|\\
+    \verb|secretArrayB| & \verb|_fs_6|\\
+    \verb|publicArray2| & \verb|_fs_7|\\
+    \verb|leak2| & \verb|_fs_9|\\
+    \hline
+  \end{tabular}
+\caption{Correspondence between EDSL names and generated C names for \ttt{example5}}
+\label{table:Names5}
+\end{table}
+
+\begin{figure}[h]
+\centering
+  \resizebox{0.3\columnwidth}{4cm}{\includegraphics{Diagrams/example5-analysis.pdf}}
+\caption{Results of leak analysis on \ttt{example5}}
+\label{fig:Analysis5}
+\end{figure}
+
 \begin{figure}[h]

### 2020-12-06 src/Security/CodeGen/C.hs

@@ -296,5 +296,5 @@ example10 = do
     ))
 
 example11 :: Cmd ()
-example11 = example8 >> example9
+example11 = example8 >> example10
 

### 2020-12-06 paper/main.tex
Fix mistake in EDSL->C table and some code formatting

@@
   \end{lstlisting}
-  & \begin{lstlisting}
+  & \begin{lstlisting}[language=C]
   int v = x;
@@
   \end{lstlisting}
-  & \begin{lstlisting}
+  & \begin{lstlisting}[language=C]
   int v[n];
@@
   \end{lstlisting}
-  & \begin{lstlisting}
+  & \begin{lstlisting}[language=C]
   int v[n] __attribute__((__nospec__));
@@
   \end{lstlisting}
-  & \begin{lstlisting}
+  & \begin{lstlisting}[language=C]
   memcpy(arrA, arrB, sizeof(arrA));
@@
   \end{lstlisting}
-  & \begin{lstlisting}
+  & \begin{lstlisting}[language=C]
   i = j;
@@
   \end{lstlisting}
-  & \begin{lstlisting}
+  & \begin{lstlisting}[language=C]
   arr[i]
@@
   \end{lstlisting}
-  & \begin{lstlisting}
+  & \begin{lstlisting}[language=C]
   x < y
@@
   \end{lstlisting}
-  & \begin{lstlisting}
+  & \begin{lstlisting}[language=C]
   while ((*@$\overline{\ttt{cond}}$@*)) { (*@$\overline{\ttt{body}}$@*) }
@@
   \begin{lstlisting}
-  if cond t f
+  ifThenElse cond t f
   \end{lstlisting}
-  & \begin{lstlisting}
+  & \begin{lstlisting}[language=C]
   if ((*@$\overline{\ttt{cond}}$@*)) { (*@$\overline{\ttt{t}}$@*) } else { (*@$\overline{\ttt{f}}$@*) }
@@
   \end{lstlisting}
-  & \begin{lstlisting}
+  & \begin{lstlisting}[language=C]
   for (int i = (*@$\overline{\ttt{init}}$@*); (*@$\overline{\ttt{cond}}$@*); (*@$\overline{\ttt{update}}$@*))
@@
   array2 <- allocSecret @Int 8
-
   array2 .= array1
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[language=Haskell]
 example3 :: Cmd ()
@@
   arrayB <- allocSecret @Int 8
-
   for (0 :: Expr Secret Int) (\i -> ((i <? 8), (i += 1), do
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[language=Haskell]
 example4 :: Cmd ()
@@
     for (0 :: Expr Secret Int) (\j -> ((j <? (secretArray ! i))
-                                      ,(j += 1)
-                                      ,do
+                                      ,(j += 1), do
       leak += 1))
@@
   publicArray <- allocPublic @Int 8
-
   for (0 :: Expr Public Int) (\i -> ((i <? 8), (i += 1), do
-
     leak <- decl (0 :: Int)
-
     for (0 :: Expr Secret Int) (\j -> ((j <? (secretArray ! i))
-                                      ,(j += 1)
-                                      ,do
-      leak += 1
-      ))
-    (publicArray ! i) .= leak
-    ))
-
+                                      ,(j += 1), do
+      leak += 1))
+    (publicArray ! i) .= leak))
   secretArrayA <- allocSecret @Int 8
@@
   publicArray2 <- allocPublic @Int 8
-
   secretArrayA .= secretArray
   secretArrayB .= secretArrayA
-
   for (0 :: Expr Public Int) (\i -> ((i <? 8), (i += 1), do
-
     leak2 <- decl (0 :: Int)
-
     for (0 :: Expr Secret Int) (\j -> ((j <? (secretArrayB ! i))
-                                      ,(j += 1)
-                                      ,do
-      leak2 += 1
-      ))
-    (publicArray2 ! i) .= leak2
-    ))
+                                      ,(j += 1), do
+      leak2 += 1)
+    (publicArray2 ! i) .= leak2))
 \end{lstlisting}

### 2020-12-07 paper/main.tex
Typing rules spacing
Better bind rule
Better naming in rule
Added 'sequence' bind rule
Future work; syntax; analysis

@@
 \newcommand{\sarr}{\leadsto}
+
+% \addtolength{\jot}{3mm}
+
 %-------------------------------------------------------------------------
@@
   A Spectre mitigation strategy in the form of a mechanism for marking variables
-  as "non-speculative" was developed in \cite{SpectreGuard}. In this paper, we
+  as ``non-speculative'' was developed in \cite{SpectreGuard}. In this paper, we
   develop an embedded domain specific language (EDSL) in Haskell to provide
@@
 
-This also outlines procedure that the C code generator uses.
+This also outlines procedure that the C code generator uses. When code written
+in the EDSL is transformed into C code, a name generator first annotates the abstract syntax tree
+(AST). This annotated AST can be used by both the code generator and the information flow
+leak analysis tool (the latter is described in Section \ref{sec:Analysis}).
 
-\begin{figure}[h]
+Code can be written in this EDSL by importing the EDSL's package in standard
+Haskell code and using the Glasgow Haskell Compiler (GHC) to compile the code.
+Note that as a result of this design, all standard Haskell programming language
+constructs are available for metaprogramming purposes.  Examples written in this
+EDSL syntax are given in Section \ref{sec:Examples}.
+
+\begin{figure}
 \begin{tabular}{|l|l|}
@@
 Singletons~\cite{SingletonsPaper} are used to preserve this type level at runtime, so that the
-code generator can generate SpectreGuard annotations where appropriate.
+code generator can generate SpectreGuard annotations where appropriate. These annotations can
+then be used by the SpectreGuard mitigation system.~\cite{SpectreGuard}
 
@@
 
-\begin{figure}[h]
+\begin{figure}
   \centering
-\resizebox{0.68\linewidth}{!}{
+\resizebox{0.67\linewidth}{!}{
 \begin{minipage}{\linewidth}
   \centering
+  \openup 3mm
 \begin{gather*}
   \inference{}{\ttt{Public :: Sensitivity}}\\
-\\
   \inference{}{\ttt{Secret :: Sensitivity}}\\
-\\
   \inference{n \in \mathbb{N}}{\ttt{$n$ :: Int}}\\
-  \\
   \inference{n \in \mathbb{N}}{\ttt{$n$ :: Expr $\sigma$ Int}}\\
-\\
   \inference{%
@@
     {\Gamma \vdash \ttt{x + y :: Expr $\sigma$ Int}}\\
-  \\
   \inference{%
@@
     {\Gamma \vdash \ttt{x <? y :: Expr $\sigma$ Bool}}\\
-  \\
   \inference{%
@@
     {\Gamma \vdash \ttt{a ! i :: Expr $\sigma$ $\tau$}}\\
-  \\
   \inference{\Gamma \vdash \ttt{n :: Int}}{\Gamma \vdash \ttt{allocPublic @$\tau$ n :: Cmd (Expr Public (Ptr $\tau$))}}\\
-\\
   \inference{\Gamma \vdash \ttt{n :: Int}}{\Gamma \vdash \ttt{allocSecret @$\tau$ n :: Cmd (Expr Secret (Ptr $\tau$))}}\\
-\\
   \inference{\Gamma \vdash \ttt{x :: $\tau$}}{\Gamma \vdash \ttt{decl x :: Cmd (Expr Public $\tau$)}}\\
-\\
   \inference{%
@@
     {\Gamma \vdash \ttt{x .= y :: Cmd ()}}\\
-  \\
   \inference{%
@@
     {\Gamma \vdash \ttt{ifThenElse cond t f :: Cmd ()}}\\
-  \\
   \inference{%
@@
     {\Gamma \vdash \ttt{while cond body :: Cmd ()}}\\
-  \\
   \inference{%
@@
     }{\Gamma \vdash \ttt{for init fn :: Cmd ()}}\\
-  \\
   \inference{%
     \Gamma \vdash \ttt{c :: Cmd (Expr $\sigma$ $\tau$)}
-    & \ttt{x} \notin dom(\Gamma)
-    \\ \Gamma \vdash \ttt{($\lambda$ x $\rarr$ body) :: Expr $\sigma$ $\tau$ $\rarr$ Cmd $\alpha$}
+    \\ \Gamma,\ttt{(x :: Expr $\sigma$ $\tau$)} \vdash \ttt{rest :: Cmd $\alpha$}
   }{%
-    \Gamma \vdash \ttt{(\textbf{do} \{ x <- c; body \}) :: Cmd $\alpha$}
+    \Gamma \vdash \ttt{(\textbf{do} \{ x <- c; rest \}) :: Cmd $\alpha$}
+  }\\
+  \inference{%
+    \Gamma \vdash \ttt{c :: Cmd (Expr $\sigma$ $\tau$)}
+    \\ \Gamma \vdash \ttt{rest :: Cmd $\alpha$}
+  }{%
+    \Gamma \vdash \ttt{(\textbf{do} \{ c; rest \}) :: Cmd $\alpha$}
   }
@@
 
-\begin{figure}[h]
+\begin{figure}
 \begin{lstlisting}{language=C}
@@
 
-\begin{figure}[h]
+\begin{figure}
 \centering
@@
 
-\begin{table}[h]
+The tree in resulting from the analysis shows that \ttt{secretArray} leaks to \ttt{leak}. Also, \ttt{secretArray} flows to
+to \ttt{secretArrayA}, which flows to \ttt{secretArrayB}. Finally, \ttt{secretArrayB} leaks to \ttt{leak2}. Once
+the analysis generates these trees, only the branches which ultimately end in a leak to a public variable
+are kept. Branches which never lead to a public variable are thrown out. Also, information flow from one
+public variable to another public variable is not represented. This choice was made to limit the size
+of the output and prevent it from being too overwhelming to the programmer.
+
+\begin{table}
   \centering
@@
 
-\begin{figure}[h]
-  \centering
-\resizebox{0.68\linewidth}{!}{
-\begin{minipage}{\linewidth}
-  \centering
-\begin{gather*}
-  \inference{%
-    \Delta;\Gamma \vdash \ttt{x :: $\tau$}
-    \\ \Delta;\Gamma \vdash \ttt{k :: Expr Public $\tau$ $\rarr$ Cmd $\alpha$}
-    \\ \Delta;\Gamma\vdash A(\ttt{decl v >>= ($\lambda$x $\rarr$ k)})
-    }
-    {%
-      \Delta,Pub(x);\Gamma \vdash A(\ttt{k})
-    }\\
-    \\
-  \inference{%
-    \Delta;\Gamma \vdash \ttt{x :: Expr Public $\tau$}
-    & \Delta;\Gamma \vdash \ttt{y :: Expr Public $\tau$}
-    \\ \Delta;\Gamma \vdash \ttt{k :: () $\rarr$ Cmd $\alpha$}
-    & \Delta;\Gamma \vdash A(\ttt{(x .= y) >>= k})
-    \\ \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
-    }
-    {%
-      \Delta;\Gamma \vdash \ttt{x} \sarr L(\ttt{x})
-    }\\
-  \\
-  \inference{%
-    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
-    & \Delta;\Gamma \vdash \ttt{body :: Cmd $\alpha$}
-    \\ \Delta;\Gamma \vdash A(\ttt{while cond body})
-    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
-    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
-    }
-    {%
-      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{body})
-    }\\
-  \\
-  \inference{%
-    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
-    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
-    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
-    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
-    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
-    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
-    }
-    {%
-      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{t})
-    }\\
-  \\
-  \inference{%
-    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
-    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
-    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
-    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
-    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
-    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
-    }
-    {%
-      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{f})
-    }\\
-  \\
-  \inference{%
-    \Delta;\Gamma \vdash v \in L(\ttt{x})
-    }
-    {%
-      \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
-    }
-\end{gather*}
-\end{minipage}}
-  \caption{Information flow analysis rules which define the relation $\sarr$}
-\label{fig:FlowRules}
-\end{figure}
+% \begin{figure}[h]
+%   \centering
+% \resizebox{0.68\linewidth}{!}{
+% \begin{minipage}{\linewidth}
+%   \centering
+% \begin{gather*}
+%   \inference{%
+%     \Delta;\Gamma \vdash \ttt{x :: $\tau$}
+%     \\ \Delta;\Gamma \vdash \ttt{k :: Expr Public $\tau$ $\rarr$ Cmd $\alpha$}
+%     \\ \Delta;\Gamma\vdash A(\ttt{decl v >>= ($\lambda$x $\rarr$ k)})
+%     }
+%     {%
+%       \Delta,Pub(x);\Gamma \vdash A(\ttt{k})
+%     }\\
+%     \\
+%   \inference{%
+%     \Delta;\Gamma \vdash \ttt{x :: Expr Public $\tau$}
+%     & \Delta;\Gamma \vdash \ttt{y :: Expr Public $\tau$}
+%     \\ \Delta;\Gamma \vdash \ttt{k :: () $\rarr$ Cmd $\alpha$}
+%     & \Delta;\Gamma \vdash A(\ttt{(x .= y) >>= k})
+%     \\ \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
+%     }
+%     {%
+%       \Delta;\Gamma \vdash \ttt{x} \sarr L(\ttt{x})
+%     }\\
+%   \\
+%   \inference{%
+%     \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
+%     & \Delta;\Gamma \vdash \ttt{body :: Cmd $\alpha$}
+%     \\ \Delta;\Gamma \vdash A(\ttt{while cond body})
+%     & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
+%     \\ \Delta;\Gamma \vdash Pub(\ttt{x})
+%     }
+%     {%
+%       \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{body})
+%     }\\
+%   \\
+%   \inference{%
+%     \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
+%     \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
+%     & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
+%     \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
+%     & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
+%     \\ \Delta;\Gamma \vdash Pub(\ttt{x})
+%     }
+%     {%
+%       \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{t})
+%     }\\
+%   \\
+%   \inference{%
+%     \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
+%     \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
+%     & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
+%     \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
+%     & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
+%     \\ \Delta;\Gamma \vdash Pub(\ttt{x})
+%     }
+%     {%
+%       \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{f})
+%     }\\
+%   \\
+%   \inference{%
+%     \Delta;\Gamma \vdash v \in L(\ttt{x})
+%     }
+%     {%
+%       \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
+%     }
+% \end{gather*}
+% \end{minipage}}
+%   \caption{Information flow analysis rules which define the relation $\sarr$}
+% \label{fig:FlowRules}
+% \end{figure}
 ...
@@
 
+More primitive operations and support for a foreign function interface (FFI)
+with C would make the EDSL more practical. This would be straightforward to add,
+as the system already closely resembles C code and generates C code.
+
+The sensitivity checking and the analysis tool could be added as an extension to
+a C compiler, via a plugin mechanism such as Clang's plugin system. This would
+have the benefits of familiarity with the language and easy interoperability
+with existing C libraries. Drawbacks would include the fact that the sensitivity type
+checking would need to be created from scratch, rather than being based on an existing, well-tested,
+type system (such as Haskell's). This would also lack the potential metaprogramming
+benefits of using an embedded DSL: creation of EDSL code can be automated using
+regular Haskell code within the EDSL. For example, a loop can be explicitly unrolled while
+at the same time preserving the brevity of using a loop.
+
 \section{Conclusion}

### 2020-12-07 src/Security/Repr.hs
Properly generate array types

@@ -20,7 +20,7 @@ data Ptr a
 data CType a where
   CInt :: CType Int
   CBool :: CType Bool
-  CPtr :: forall a. CType a -> CType (Ptr a)
+  CPtr :: forall a. Repr a => CType a -> CType (Ptr a)
 
 deriving instance Show (CType a)
 
@@ -64,7 +64,10 @@ genDecl sizeMaybe ty n =
   where
     leftPart =
       case sizeMaybe of
-        Just size -> unwords [typeRepr ty, emitName n <> "[" <> show size <> "]"]
+        Just size ->
+          case ty of
+            CPtr ty' -> unwords [typeRepr ty', emitName n <> "[" <> show size <> "]"]
+            _ -> error "size given with a non-pointer type"
         _ -> unwords [typeRepr ty, emitName n]
 
 

### 2020-12-07 paper/main.tex
Reflect proper array type generation in paper

@@
 \begin{lstlisting}{language=C}
-int* _fs_0[8] __attribute__((nospec))__;
-int* _fs_1[8];
+int _fs_0[8] __attribute__((nospec))__;
+int _fs_1[8];
 for (int _fs_2 = 0; _fs_2 < 8; _fs_2 = _fs_2 + 1) {
   int _fs_3 = 0;
-  for (int _fs_4 __attribute__((nospec))__ = 0;
-       _fs_4 < (_fs_0[_fs_2]);
-       _fs_4 = _fs_4 + 1) {
+  for (int _fs_4 __attribute__((nospec))__ = 0; _fs_4 < (_fs_0[_fs_2]); _fs_4 = _fs_4 + 1) {
     _fs_3 = _fs_3 + 1;
@@
     \hline
-    EDSL name & Generated C Name \\
+    EDSL name in \ttt{example5} & Generated C Name \\
     \hline

### 2020-12-07 paper/main.tex
Reformat generated code in paper

@@
   int _fs_3 = 0;
-  for (int _fs_4 __attribute__((nospec))__ = 0; _fs_4 < (_fs_0[_fs_2]); _fs_4 = _fs_4 + 1) {
+  for (int _fs_4 __attribute__((nospec))__ = 0 ;
+      fs_4 < (_fs_0[_fs_2]);
+      _fs_4 = _fs_4 + 1) {
     _fs_3 = _fs_3 + 1;

### 2020-12-07 paper/main.tex
More on sensitivity types. Foreshadow analysis section

@@
 \section{Sensitivity Types}
-The Haskell type system is leveraged to perform a basic static consistency check of the sensitivities
-of variables, so that a variable does not get assigned to a variable of a different sensitivity. This
-is done by making the \verb|Expr| type constructor take a phantom type argument~\cite{Phantom}. The
-logical inference rules corresponding to this check are given in Fig. \ref{fig:SensTypes}. An introduction
-to this style of inference rule system, with many examples and applications in the study of programming languages, is given in \cite{HarperFoundations}.
+The Haskell type system is leveraged to perform a basic static consistency check
+of the sensitivities of variables, so that a variable does not get assigned to a
+variable of a different sensitivity. This is done by making the \verb|Expr| type
+constructor take a phantom type argument~\cite{Phantom}. The phantom type
+argument is the \textit{sensitivity type} of that expression.  The logical
+inference rules corresponding to this check are given in Fig.
+\ref{fig:SensTypes}. Note that the EDSL inherits the rest of Haskell's type
+system in addition to these rules. Only the aspects of the type system that is
+particularly relevant to the EDSL is reflected in the figure, often specialized
+to the particular scenario encountered in using sensitivity types in the EDSL.
+An introduction to this style of inference rule system, with many examples and
+applications in the study of programming languages, is given in
+\cite{HarperFoundations}.
+
+Observe that an two expressions with different sensitivity types cannot be
+combined into a larger compound expression. However, commands (represented by
+the \verb|Cmd| type constructor) often have expressions embedded in them and
+commands can be sequenced with each other.  There is no restriction on how two
+commands can be combined, even if they involve expressions with different
+sensitivity types. This freedom in combining commands independently of
+sensitivity foreshadows the essence of the problem we will encounter in
+Section \ref{sec:Analysis}. For now, note that all control flow constructs are
+part of the command type (as opposed to the expression type).
 
@@
 
-A typing judgement is expressed with the syntax
+\noindent A typing judgement is expressed with the syntax
 
@@
 
-where \ttt{x} is some expression or command in the EDSL. This judgement means
+\noindent where \ttt{x} is some expression or command in the EDSL. This judgement means
 that \ttt{x} has type $\beta$. This is also the same syntax used by Haskell, and by extension

### 2020-12-07 paper/main.tex
Center generated code figure
Barendregt convention

@@
 This also outlines procedure that the C code generator uses. When code written
-in the EDSL is transformed into C code, a name generator first annotates the abstract syntax tree
-(AST). This annotated AST can be used by both the code generator and the information flow
-leak analysis tool (the latter is described in Section \ref{sec:Analysis}).
+in the EDSL is transformed into C code, a name generator first annotates the
+abstract syntax tree (AST) with globally unique names (enforcing the Barendregt
+variable convention; see Chapter 2 in~\cite{BarendregtConversion}). This annotated AST can be used by both the code generator and the
+information flow leak analysis tool (the latter is described in Section
+\ref{sec:Analysis}).
 
@@
 \begin{figure}
+\begin{center}
+\begin{tabular}{c}
 \begin{lstlisting}{language=C}
@@
 \end{lstlisting}
+\end{tabular}
+\end{center}
 \caption{C code generated from \ttt{example4}}

### 2020-12-07 paper/main.tex
Clarify generated code slightly
Add more horizontal lines to naming table
wibble

@@
 int _fs_1[8];
-for (int _fs_2 = 0; _fs_2 < 8; _fs_2 = _fs_2 + 1) {
+for (int _fs_2 = 0; _fs_2 < 8; _fs_2 = _fs_2 + 1)
+{
   int _fs_3 = 0;
@@
       fs_4 < (_fs_0[_fs_2]);
-      _fs_4 = _fs_4 + 1) {
+      _fs_4 = _fs_4 + 1)
+  {
     _fs_3 = _fs_3 + 1;
@@
     \verb|secretArray| & \verb|_fs_0|\\
+    \hline
     \verb|publicArray| & \verb|_fs_1|\\
+    \hline
     \verb|leak| & \verb|_fs_3|\\
+    \hline
     \verb|secretArrayA| & \verb|_fs_5|\\
+    \hline
     \verb|secretArrayB| & \verb|_fs_6|\\
+    \hline
     \verb|publicArray2| & \verb|_fs_7|\\
+    \hline
     \verb|leak2| & \verb|_fs_9|\\
@@
 
+\section{Related Work}
+...
+
 \section{Future Work}
@@
 Dependent types provide a powerful technique for writing programs at a type-level, which
-will be executed at compile-time by the type checker.~\cite{CertProg}
+will be executed at compile-time by the type checker.~\cite{CertProg, DepHaskSpec}
 

### 2020-12-08 paper/main.tex
wibble

@@
   \tau ::= \ttt{Int}\;|\;\ttt{Ptr}\;\tau\\
-  \alpha ::= \ttt{Cmd ()}\;|\;\ttt{Cmd (Expr $\sigma$ $\tau$)}
+  \alpha ::= \ttt{()}\;|\;\ttt{Expr $\sigma$ $\tau$}
 \end{gather*}
@@
     \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
-    &\Gamma \vdash \ttt{t :: $\tau$}
-    &\Gamma \vdash \ttt{f :: $\tau$}}
+    &\Gamma \vdash \ttt{t :: Cmd $\alpha$}
+    &\Gamma \vdash \ttt{f :: Cmd $\alpha$}}
     {\Gamma \vdash \ttt{ifThenElse cond t f :: Cmd ()}}\\
@@
   int _fs_3 = 0;
-  for (int _fs_4 __attribute__((nospec))__ = 0 ;
+  for (int _fs_4 __attribute__((nospec))__ = 0;
       fs_4 < (_fs_0[_fs_2]);

### 2020-12-08 paper/main.tex
Starting an attempt at pseudocode for the information flow analysis

@@
 
+\begin{figure}
+\begin{lstlisting}[language=Haskell]
+analyze(forest, scope, return x) = forest
+analyze(forest, scope, (do { n <- allocPublic @ty size; r n })) = do
+  scope.insert(Public, n)
+  analyze(forest, scope, r(n))
+
+analyze(forest, scope, (do { n <- allocSecret @ty size; r n })) = do
+  scope.insert(Secret, n)
+  analyze(forest, scope, r(n))
+
+analyze(forest, scope, (do { n <- decl x; r n })) = do
+  scope.insert(Public, n)
+  analyze(forest, scope, r(n))
+
+analyze(forest, scope, (do { x .= y; r })) = do
+  let lhsNames = collectExprNames(x)
+  let rhsNames = collectExprNames(y)
+
+  foreach rhsName in rhsNames
+    if (rhsName is secret)
+      forest.addChildrenTo(rhsName, lhsNames)
+    end
+  end
+
+  foreach lhsName in lhsNames
+    let scopeFrame = scope.getScopeFrameOf(lhsName)
+
+    if scope.notCurrentScopeFrame(scopeFrame)
+      forest.addChildrenTo(lhsName, scopeFrame.secretVariables)
+    end
+  end
+
+  analyze(forest, scope, r)
+
+analyze(forest, scope, (do { ifThenElse cond t f; r })) = do
+  let secretNames = filter(isSecretName, collectExprNames(cond))
+
+  let tForest = copy(forest)
+  let fForest = copy(forest)
+  let tScope = copy(scope)
+  let fScope = copy(scope)
+
+  analyze(tForest, tScope.pushFrame(secretNames), r)
+  analyze(fForest, fScope.pushFrame(secretNames), r)
+
+  forest = union(tForest, fForest)
+  analyze(forest, scope, r)
+\end{lstlisting}
+\caption{Information leak analysis pseudocode}
+\end{figure}
+
 % \begin{figure}[h]

### 2020-12-09 paper/main.tex
More explanation of the analysis

--- 2020-12-08 paper/main.tex
@@
     \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
-    &\Gamma \vdash \ttt{t :: Cmd $\alpha$}
+    \\ \Gamma \vdash \ttt{t :: Cmd $\alpha$}
     &\Gamma \vdash \ttt{f :: Cmd $\alpha$}}
@@
 
+The implementation of the analysis tool is built around two primary data
+structures:
+
+\begin{itemize}
+  \item
+    A forest of multi-way trees (these are also called ``rose
+trees''~\cite{LooplessBird}) which represents the leak paths
+  \item
+    A stack of name associations (a ``scope stack''). Each entry in the stack is
+    a pair consisting of two lists of names. The first list contains all of the
+    names that are in the current scope: the ``in-scope list''. When a
+    conditional construct is entered, all of the secret variables in the
+    conditional will be put into the second list and a new pair of empty lists
+    will be pushed onto the stack. This second list is the ``secret list''
+\end{itemize}
+
+When a declaration is encountered, this name is added to the current ``scope
+frame'' in the scope stack. Whenever an assignment is encountered, all of the
+names in the left-hand side which are contained in the in-scope list of any
+scope frame \textit{before} the current one are added as children (in the rose
+tree forest) of all of nodes corresponding to the names in the secret list of
+the stack frame in which the left-hand side name occured.
+
+At the end of the algorithm, only leaves corresponding to public names are
+retained.
+
+% \begin{figure}
+% \begin{lstlisting}[language=Haskell]
+% analyze(forest, scope, return x) = forest
+% analyze(forest, scope, (do { n <- allocPublic @ty size; r n })) = do
+%   scope.insert(Public, n)
+%   analyze(forest, scope, r(n))
+
+% analyze(forest, scope, (do { n <- allocSecret @ty size; r n })) = do
+%   scope.insert(Secret, n)
+%   analyze(forest, scope, r(n))
+
+% analyze(forest, scope, (do { n <- decl x; r n })) = do
+%   scope.insert(Public, n)
+%   analyze(forest, scope, r(n))
+
+% analyze(forest, scope, (do { x .= y; r })) = do
+%   let lhsNames = collectExprNames(x)
+%   let rhsNames = collectExprNames(y)
+
+%   foreach rhsName in rhsNames
+%     if (rhsName is secret)
+%       forest.addChildrenTo(rhsName, lhsNames)
+%     end
+%   end
+
+%   foreach lhsName in lhsNames
+%     let scopeFrame = scope.getScopeFrameOf(lhsName)
+
+%     if scope.notCurrentScopeFrame(scopeFrame)
+%       forest.addChildrenTo(lhsName, scopeFrame.secretVariables)
+%     end
+%   end
+
+%   analyze(forest, scope, r)
+
+% analyze(forest, scope, (do { ifThenElse cond t f; r })) = do
+%   let secretNames = filter(isSecretName, collectExprNames(cond))
+
+%   let tForest = copy(forest)
+%   let fForest = copy(forest)
+%   let tScope = copy(scope)
+%   let fScope = copy(scope)
+
+%   analyze(tForest, tScope.pushFrame(secretNames), r)
+%   analyze(fForest, fScope.pushFrame(secretNames), r)
+
+%   forest = union(tForest, fForest)
+%   analyze(forest, scope, r)
+% \end{lstlisting}
+% \caption{Information leak analysis pseudocode}
+% \end{figure}
+
 % \begin{figure}[h]

### 2020-12-09 paper/main.tex
Introduction

@@
 
-% \addtolength{\jot}{3mm}
-
 %-------------------------------------------------------------------------
@@
 \section{Introduction}
-Introduction goes here.
+SpectreGuard is provides an abstraction that allows programmers to prevent
+speculative access of certain variables.~\cite{SpectreGuard} For
+preserving program correctness, static analyses are desirable to prevent
+programmers from accidentally successfully compiling code which copies a
+``secret'' variable (a variable protected by SpectreGuard) to a ``public''
+variable (a variable with no such protection).
+
+To this end, two interrelated static analysis techniques are designed and
+implemented. In this paper, we make the following contributions:
+
+\begin{itemize}
+\item We describe a small domain specific language embedded in Haskell for representing
+  simple C programs (Section~\ref{sec:Syntax}).
+\item A code generator which generates C code from this EDSL is outlined
+  (Section~\ref{sec:Syntax}).
+\item We give a system of types which causes the expression language of this
+  EDSL to be statically checked for variable copies that directly leak memory
+  from secret variables to public variables (Section~\ref{sec:SensTypes}).
+\item Another static analysis procedure is given which can find \textit{indirect}
+  leak paths through control structures (Section~\ref{sec:Analysis}). This analysis
+  procedure can be applied to EDSL code in the same way as the code generator
+  can be applied to EDSL code. The results from this analysis take the form
+  of a forest of multiway trees, providing information about these possible
+  indirect leaks.
+\end{itemize}
 
@@
 \section{Syntax}
+\label{sec:Syntax}
 A correspondence between the syntax of the EDSL, which is inherited from
@@
 
-% \begin{figure}
-% \begin{lstlisting}[language=Haskell]
-% analyze(forest, scope, return x) = forest
-% analyze(forest, scope, (do { n <- allocPublic @ty size; r n })) = do
-%   scope.insert(Public, n)
-%   analyze(forest, scope, r(n))
-
-% analyze(forest, scope, (do { n <- allocSecret @ty size; r n })) = do
-%   scope.insert(Secret, n)
-%   analyze(forest, scope, r(n))
-
-% analyze(forest, scope, (do { n <- decl x; r n })) = do
-%   scope.insert(Public, n)
-%   analyze(forest, scope, r(n))
-
-% analyze(forest, scope, (do { x .= y; r })) = do
-%   let lhsNames = collectExprNames(x)
-%   let rhsNames = collectExprNames(y)
-
-%   foreach rhsName in rhsNames
-%     if (rhsName is secret)
-%       forest.addChildrenTo(rhsName, lhsNames)
-%     end
-%   end
-
-%   foreach lhsName in lhsNames
-%     let scopeFrame = scope.getScopeFrameOf(lhsName)
-
-%     if scope.notCurrentScopeFrame(scopeFrame)
-%       forest.addChildrenTo(lhsName, scopeFrame.secretVariables)
-%     end
-%   end
-
-%   analyze(forest, scope, r)
-
-% analyze(forest, scope, (do { ifThenElse cond t f; r })) = do
-%   let secretNames = filter(isSecretName, collectExprNames(cond))
-
-%   let tForest = copy(forest)
-%   let fForest = copy(forest)
-%   let tScope = copy(scope)
-%   let fScope = copy(scope)
-
-%   analyze(tForest, tScope.pushFrame(secretNames), r)
-%   analyze(fForest, fScope.pushFrame(secretNames), r)
-
-%   forest = union(tForest, fForest)
-%   analyze(forest, scope, r)
-% \end{lstlisting}
-% \caption{Information leak analysis pseudocode}
-% \end{figure}
-
-% \begin{figure}[h]
-%   \centering
-% \resizebox{0.68\linewidth}{!}{
-% \begin{minipage}{\linewidth}
-%   \centering
-% \begin{gather*}
-%   \inference{%
-%     \Delta;\Gamma \vdash \ttt{x :: $\tau$}
-%     \\ \Delta;\Gamma \vdash \ttt{k :: Expr Public $\tau$ $\rarr$ Cmd $\alpha$}
-%     \\ \Delta;\Gamma\vdash A(\ttt{decl v >>= ($\lambda$x $\rarr$ k)})
-%     }
-%     {%
-%       \Delta,Pub(x);\Gamma \vdash A(\ttt{k})
-%     }\\
-%     \\
-%   \inference{%
-%     \Delta;\Gamma \vdash \ttt{x :: Expr Public $\tau$}
-%     & \Delta;\Gamma \vdash \ttt{y :: Expr Public $\tau$}
-%     \\ \Delta;\Gamma \vdash \ttt{k :: () $\rarr$ Cmd $\alpha$}
-%     & \Delta;\Gamma \vdash A(\ttt{(x .= y) >>= k})
-%     \\ \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
-%     }
-%     {%
-%       \Delta;\Gamma \vdash \ttt{x} \sarr L(\ttt{x})
-%     }\\
-%   \\
-%   \inference{%
-%     \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
-%     & \Delta;\Gamma \vdash \ttt{body :: Cmd $\alpha$}
-%     \\ \Delta;\Gamma \vdash A(\ttt{while cond body})
-%     & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
-%     \\ \Delta;\Gamma \vdash Pub(\ttt{x})
-%     }
-%     {%
-%       \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{body})
-%     }\\
-%   \\
-%   \inference{%
-%     \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
-%     \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
-%     & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
-%     \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
-%     & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
-%     \\ \Delta;\Gamma \vdash Pub(\ttt{x})
-%     }
-%     {%
-%       \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{t})
-%     }\\
-%   \\
-%   \inference{%
-%     \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
-%     \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
-%     & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
-%     \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
-%     & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
-%     \\ \Delta;\Gamma \vdash Pub(\ttt{x})
-%     }
-%     {%
-%       \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{f})
-%     }\\
-%   \\
-%   \inference{%
-%     \Delta;\Gamma \vdash v \in L(\ttt{x})
-%     }
-%     {%
-%       \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
-%     }
-% \end{gather*}
-% \end{minipage}}
-%   \caption{Information flow analysis rules which define the relation $\sarr$}
-% \label{fig:FlowRules}
-% \end{figure}
-...
-
-% \section{Your System}
-% ...
-% \section{Evaluation}
-% ...
-
 \section{Related Work}

### 2020-12-09 paper/main.tex
Fix reference

@@
 \section{Sensitivity Types}
+\label{sec:SensTypes}
 The Haskell type system is leveraged to perform a basic static consistency check

### 2020-12-09 paper/main.tex
starting related work; 'ghosts of departed proofs

@@
 ``secret'' variable (a variable protected by SpectreGuard) to a ``public''
-variable (a variable with no such protection).
+variable (a variable with no such protection). To this end, two interrelated static analysis techniques are designed and
+implemented.
 
-To this end, two interrelated static analysis techniques are designed and
-implemented. In this paper, we make the following contributions:
+In this paper, we make the following contributions:
 
@@
   indirect leaks.
+\item We provide several examples and describe how the system handles them
+  (Section~\ref{sec:Examples}).
 \end{itemize}
@@
 \section{Related Work}
-...
+The way that the type-level tagging mechanism works is similar to several other
+prior works. One such work is McBride's "Kleisli Arrows of Outrageous Fortune"~\cite{KleisliArrows}. In that paper, an invalid state is unable to be reached as the result of
+a similar type-level tag as the \ttt{Sensitivity} tag in the present paper.
+However, significantly more machinery is involved in the McBride paper, as
+it is necessary to put such a tag on a monadic type. While a monadic type is
+used in the present paper (in the form of the \ttt{Cmd} type), this type
+does not use a type-level tag. The creation of such machinery is the
+main purpose of the McBride paper.
 
@@
 could be incorporated into the type system, by exploiting the dependent type
-features enabled by singletons~\cite{SingletonsPaper} and, in the future, by Dependent Haskell.~\cite{DepHaskSpec}
-Dependent types provide a powerful technique for writing programs at a type-level, which
-will be executed at compile-time by the type checker.~\cite{CertProg, DepHaskSpec}
+features enabled by singletons~\cite{SingletonsPaper} and, in the future, by
+Dependent Haskell.~\cite{DepHaskSpec} Dependent types provide a powerful
+technique for writing programs at a type-level, which will be executed at
+compile-time by the type checker.~\cite{CertProg, DepHaskSpec} A more
+lightweight technique, which might be able to be applied to allow for more
+expressive policies to control of information flow within the type system, would
+be the ``ghosts of departed proofs'' design technique.~\cite{DepartedProofs}
 
@@
 \section{Conclusion}
-...
+
+Building upon the SpectreGuard work~\cite{SpectreGuard}, we have constructed
+a system which allows the programmer greater assurance that the SpectreGuard
+mechanism will not be accidentally circumvented due to certain forms of
+leaks from secret variables to public variables. This analysis checks for
+both direct copies from a secret variable to a public variable, as well as
+a certain class of leaks where control flow depends on a secret variable.
+
+SpectreGuard is a powerful tool for protecting code against Spectre attacks and,
+in the present work, we have given tools which provide additional guarantees
+that this tool will function as intended.
+
 %-------------------------------------------------------------------------

### 2020-12-11 paper/main.tex
Intro; background; related work; future work

@@
 \section{Introduction}
+\label{sec:Introduction}
 SpectreGuard is provides an abstraction that allows programmers to prevent
-speculative access of certain variables.~\cite{SpectreGuard} For
+speculative access of certain variables.~\cite{SpectreGuard} As Spectre-based
+attacks remain an issue, even in modern computer systems, such mitigations and
+preventative measures are crucial to maintaining the security of software.  For
 preserving program correctness, static analyses are desirable to prevent
@@
 ``secret'' variable (a variable protected by SpectreGuard) to a ``public''
-variable (a variable with no such protection). To this end, two interrelated static analysis techniques are designed and
-implemented.
+variable (a variable with no such protection). To this end, two interrelated
+static analysis techniques are designed and implemented.
 
@@
 \section{Background}
-Cite a paper. % \cite{barroso2009datacenter}.
 
-Cite multiple papers. % \cite{banga99resourcecontainers,barroso2009datacenter}
+Haskell is a purely functional programming language with strong static type system
+based on System F and algebraic datatypes (ADTs).~\cite{HistoryOfHaskell} These features,
+particularly the type system and the algebraic datatypes, make it a powerful tool
+for the creation of EDSLs. Expressions, commands and programs (compound commands)
+can be straightforwardly expressed using ADTs using a \textit{deep embedding}.~\cite{DeepAndShallow}
+
+A deep embedding directly exposes its abstract syntax tree (AST) as a value.
+This allows EDSL programs to be easily manipulated and examined, such as for
+interpretation, code generation and static analysis (the latter two we make use
+of in this paper).
 
@@
 \ref{sec:Analysis}).
+
+The one major aspect of the C code generator that is not described in this table
+is how the loop variable in \ttt{for} loops can be tagged as secret (if appropriate).
+This is accomplished by recovering the type-level sensitivity type information at
+runtime. Such a recovery is made possible by the use of singletons.~\cite{Singletons}
 
@@
 
+An alternate way to view the scope stack is as a stack of \textit{relations} on
+on names. Each item of the stack is a relation such that two names are related
+if and only if the left-hand name is a public variable declared in the corresponding
+scope and the right-hand name is a secret variable in a conditional within the scope.
+
+This allows us to look for leaks that happen ``through'' a control construct.
+
+The operations on the scope stack data structure have the following type signatures:
+
+\begin{lstlisting}
+emptyScope :: Scope
+
+scopeAddName :: Scope -> Name -> Scope
+scopePush :: Scope -> [Name] -> Scope
+scopePop :: Scope -> Scope
+publicNonLocals :: Scope -> Name -> Maybe [Name]
+\end{lstlisting}
+
+These operations are used by the tool in its analysis of an EDSL
+program as follows:
+
+Whenever a declaration is encountered in EDSL code, the corresponding variable
+name is added to the scope stack with \ttt{scopeAddName}. Whenever a control
+structure is entered (such as a \ttt{for} loop or an \ttt{if} statement),
+\ttt{scopePush} is called with a list of all secret variables (if any) in the
+condition of that control structure. When an assignment is encountered, it
+uses \ttt{publicNonLocals} to see if there are any secret variables associated
+to an enclosing control structure, outside of which the given name has been declared.
+
 At the end of the algorithm, only leaves corresponding to public names are
-retained.
+retained. This is due to the fact that the only time a leak occurs, from the
+perspective of this static analysis tool, is if a secret variable eventually
+gets indirectly copied to a public variable.
 
 \section{Related Work}
+\label{sec:RelatedWork}
+
 The way that the type-level tagging mechanism works is similar to several other
-prior works. One such work is McBride's "Kleisli Arrows of Outrageous Fortune"~\cite{KleisliArrows}. In that paper, an invalid state is unable to be reached as the result of
-a similar type-level tag as the \ttt{Sensitivity} tag in the present paper.
-However, significantly more machinery is involved in the McBride paper, as
-it is necessary to put such a tag on a monadic type. While a monadic type is
-used in the present paper (in the form of the \ttt{Cmd} type), this type
-does not use a type-level tag. The creation of such machinery is the
-main purpose of the McBride paper.
+prior works. One such work is McBride's \textit{Kleisli Arrows of Outrageous
+Fortune}~\cite{KleisliArrows}. In that paper, an invalid state is unable to be
+reached as the result of a similar type-level tag as the \ttt{Sensitivity} tag
+in the present paper: the McBride paper uses a type-level tag which indicates
+whether a file handle is open or closed. However, significantly more machinery
+is involved in the McBride paper, as it is necessary to put such a tag on a
+monadic type. While a monadic type is used in the present paper (in the form of
+the \ttt{Cmd} type), this type does not use a type-level tag. The creation of
+such machinery is the main purpose of the McBride paper.
+
+A significant recent work also related to the use of domain specific languages
+with strong, static type systems to control information flow for security
+purposes is \textit{Liquid Information Flow Control} by Polikarpova et
+al.~\cite{Lifty} In this work, a novel domain specific programming language is
+developed which has a static type system that is geared specifically towards
+expressing security policies at a type level. As this is done within a static
+type system, these invariants are machine-verified at compile-time.  Not only
+can these policy violations be detected, the system they develop is also able to
+fix leaks.
 
 \section{Future Work}
+\label{sec:FutureWork}
 A further investigation into the tradeoffs and possible additional features of
@@
 be the ``ghosts of departed proofs'' design technique.~\cite{DepartedProofs}
+
+Another possible, related, future development would be the to attempt to add a
+mechanism which automatically fixes some (or all) leaks. Such a system has precendent
+in the previously mentioned paper \textit{Liquid Information Flow Control}.~\cite{Lifty}
+This could give programmers an additional tool towards ensuring correctness, with
+respect to SpectreGuard annotations.
 
@@
 \section{Conclusion}
+\label{sec:Conclusion}
 

### 2020-12-11 src/Security/CodeGen/C.hs

@@ -9,6 +9,7 @@
 module Security.CodeGen.C
   where
 
+
 import           Security.Repr
 import           Security.Types
 import           Security.Sensitivity
@@ -270,7 +271,7 @@ example10 = do
 
   for (0 :: Expr Public Int) (\i -> ((i <? 8), (i += 1), do
 
-    leak <- decl (0 :: Int)
+    leak <- decl 0
 
     for (0 :: Expr Secret Int) (\j -> ((j <? (secretArray ! i)), (j += 1), do
       leak += 1
@@ -297,4 +298,11 @@ example10 = do
 
 example11 :: Cmd ()
 example11 = example8 >> example10
+
+example3_ :: Cmd ()
+example3_ = do
+  arr <- allocSecret @Int 8
+
+  for (0 :: Expr Secret Int) (\i -> (i <? 8, i += 1, do
+    (arr ! i) .= 7))
 

### 2020-12-11 paper/main.tex
Intro; upcoming pattern matching paper citation

@@
 
-Haskell is a purely functional programming language with strong static type system
-based on System F and algebraic datatypes (ADTs).~\cite{HistoryOfHaskell} These features,
-particularly the type system and the algebraic datatypes, make it a powerful tool
-for the creation of EDSLs. Expressions, commands and programs (compound commands)
-can be straightforwardly expressed using ADTs using a \textit{deep embedding}.~\cite{DeepAndShallow}
+Haskell is a purely functional programming language with strong static type
+system based on System F and algebraic datatypes (ADTs).~\cite{HistoryOfHaskell}
+These features, particularly the type system, the algebraic datatypes and its
+support for higher-order functions, make it a powerful tool for the creation of
+EDSLs. Expressions, commands and programs (compound commands) can be
+straightforwardly expressed using ADTs using a \textit{deep
+embedding}.~\cite{DeepAndShallow}
 
@@
 abstract syntax tree (AST) with globally unique names (enforcing the Barendregt
-variable convention; see Chapter 2 in~\cite{BarendregtConversion}). This annotated AST can be used by both the code generator and the
-information flow leak analysis tool (the latter is described in Section
-\ref{sec:Analysis}).
+variable convention; see Chapter 2 in~\cite{BarendregtConversion}). This
+annotated AST can be used by both the code generator and the information flow
+leak analysis tool (the latter is described in Section \ref{sec:Analysis}). It
+is worth noting that, as a result of this technique, the names in the generated
+C code will not generally be the same as the names in the EDSL code.
 
@@
 runtime. Such a recovery is made possible by the use of singletons.~\cite{Singletons}
+\ttt{for} loops provide a particular example of where Haskell's support for higher-order function
+can be used inside an EDSL to implement commands that involve the creation of
+new variables.
 
@@
 
-Singletons~\cite{SingletonsPaper} are used to preserve this type level at runtime, so that the
+Singletons~\cite{Singletons} are used to preserve this type level at runtime, so that the
 code generator can generate SpectreGuard annotations where appropriate. These annotations can
@@
 
-These operations are used by the tool in its analysis of an EDSL
+\noindent These operations are used by the tool in its analysis of an EDSL
 program as follows:
@@
 could be incorporated into the type system, by exploiting the dependent type
-features enabled by singletons~\cite{SingletonsPaper} and, in the future, by
+features enabled by singletons~\cite{Singletons} and, in the future, by
 Dependent Haskell.~\cite{DepHaskSpec} Dependent types provide a powerful
@@
 going the other direction could be provided by an instruction in the EDSL
-which might perform a Spectre mitigation measure, such as a cache flush. \cite{PLtea-james}
+which might perform a Spectre mitigation measure, such as a cache flush.~\cite{PLtea-james}
 
@@
 with C would make the EDSL more practical. This would be straightforward to add,
-as the system already closely resembles C code and generates C code.
+as the system already closely resembles C code and generates C code. This could allow
+for better integration between code written in the EDSL and regular C code. One potential
+practical application of this is that the security-critical portion of a program
+can be written in this EDSL and the rest of the application can be written as a regular
+C program which interacts with the security-critical portion via an FFI going from C to
+the EDSL and an FFI going the other direction.
+
+Additional primitive operations added to the EDSL could include higher-level language features, such as higher-order
+functions, algebraic data types, pattern matching and tail recursion. An implementation path for
+these features is described in the upcoming paper \textit{On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages}, by
+David Young, Mark Grebe and Andy Gill.~\cite{PatMatchingEDSL}
 
@@
 
-SpectreGuard is a powerful tool for protecting code against Spectre attacks and,
+SpectreGuard is a powerful mechanism for protecting code against Spectre attacks and,
 in the present work, we have given tools which provide additional guarantees
-that this tool will function as intended.
+that this mechanism will function as intended.
 

### 2020-12-11 paper/main.tex
wibble
Winskel; prior work on the theory of information flow

@@
 result of information being indirectly leaked from the secret variable to the
-public variable via a control flow construct: in this case, the innermost \ttt{for} loop.
+public variable via a control flow construct: in this case, the innermost \ttt{for} loop. Such an example has been studied from programming language perspective before; for instance
+in~\cite{InfoFlowAnalysis}.
 
@@
 
-A more complicated example is \ttt{example6} in the following:
+A more complicated example is \ttt{example5} in the following:
 
@@
 
+As mentioned previously, a theory of \textit{information flow} in the context of
+both computer security and programming languag theory has been developed. A description
+of this theory is given in~\cite{InfoFlowAnalysis}.
+
 A significant recent work also related to the use of domain specific languages
@@
 fix leaks.
+
+More broadly, a similar example of a language being represented similarly, as an
+pure expression language separated from a command language, can be found in
+Winskel's 1993 book in the form of the \textbf{IMP} language.\cite{WinskelBook} This
+book provides an in-depth look at the three major mathematical formalizations
+of programming language semantics (axiomatic semantics, operational semantics and
+denotational semantics) and uses them to analyze \textbf{IMP}
 
@@
 
+Other possible leak paths should also be investigated. While outside the scope of this paper,
+it there could be leaks which occur under circumstances other than direct copies or the indirect
+leaks described in Section~\ref{sec:Analysis}. In future work, it would be useful to either
+classify more leak paths (and deal with them appropriately) or prove that, in fact, no such additional
+leak paths exist (at least, within a certain threat model).
+
+A related topic would be enriching the theoretical background of the leak analysis tool. The theory of
+programming language semantics, particularly denotational semantics and operational semantics~\cite{WinskelBook}, as well
+as the theory of information flow~\cite{InfoFlowAnalysis}, would be particularly applicable here.
+
 \section{Conclusion}

### 2020-12-11 paper/main.tex
wibble

@@
 As mentioned previously, a theory of \textit{information flow} in the context of
-both computer security and programming languag theory has been developed. A description
+both computer security and programming language theory has been developed. A description
 of this theory is given in~\cite{InfoFlowAnalysis}.
@@
 purposes is \textit{Liquid Information Flow Control} by Polikarpova et
-al.~\cite{Lifty} In this work, a novel domain specific programming language is
+al.~\cite{Lifty} As its title suggests, this paper also builds on the theory of information flow. In that work, a novel domain specific programming language is
 developed which has a static type system that is geared specifically towards
@@
 
-More broadly, a similar example of a language being represented similarly, as an
+More broadly, an example of a language being represented similarly, as an
 pure expression language separated from a command language, can be found in
-Winskel's 1993 book in the form of the \textbf{IMP} language.\cite{WinskelBook} This
+Winskel's 1993 book in the form of the \textbf{IMP} language.~\cite{WinskelBook} This
 book provides an in-depth look at the three major mathematical formalizations
 of programming language semantics (axiomatic semantics, operational semantics and
-denotational semantics) and uses them to analyze \textbf{IMP}
+denotational semantics) and uses them to analyze \textbf{IMP}.
 

### 2020-12-11 paper/main.tex
paper: 'obfuscate' operations and conditional entropy

@@
 
+Another possible avenue of future work is the creation of ``obfuscate''
+operations: operations which change the contents of secret variable in such a
+way that it is not feasible to recover the original contents. An example is a
+hash function. This could be a mechanism to go from a secret variable to a
+public variable. The type system and analysis tool could then be modified to
+account for this. Perhaps it is also possible to allow the programmer to create
+new obfuscate functions, maybe using a restricted subset of the language. Also,
+it might be possible to use information theory concepts, like the conditional
+entropy~\cite{InfoTheory} of the function output conditioned on its input, to create a framework
+to statically provide assurance that there is a certain limit on how much
+information could be theoretically recovered (in general) after such a
+programmer-defined obfuscate function is applied.
+
 \section{Conclusion}

### 2020-12-11 paper/main.tex
done with paper?

@@
 annotated AST can be used by both the code generator and the information flow
-leak analysis tool (the latter is described in Section \ref{sec:Analysis}). It
-is worth noting that, as a result of this technique, the names in the generated
-C code will not generally be the same as the names in the EDSL code.
+leak analysis tool (the latter is described in Section \ref{sec:Analysis}). The
+code generator performs a transformation from code in the syntax given in the
+left column of Fig.~\ref{fig:Syntax} to the right column of the figure. This is
+transformation recursively applies itself when it reaches the parts marked with
+an overline in the right column of the figure. It is worth noting that, as a
+result of this technique, the names in the generated C code will not generally
+be the same as the names in the EDSL code.
 
@@
 \end{figure}
-
-...
 
@@
 going the other direction could be provided by an instruction in the EDSL
-which might perform a Spectre mitigation measure, such as a cache flush.~\cite{PLtea-james}
+which might perform a Spectre mitigation measure, such as a cache flushes at appropriate times.~\cite{PLtea-james}
 
@@
 operations: operations which change the contents of secret variable in such a
-way that it is not feasible to recover the original contents. An example is a
-hash function. This could be a mechanism to go from a secret variable to a
-public variable. The type system and analysis tool could then be modified to
-account for this. Perhaps it is also possible to allow the programmer to create
-new obfuscate functions, maybe using a restricted subset of the language. Also,
-it might be possible to use information theory concepts, like the conditional
-entropy~\cite{InfoTheory} of the function output conditioned on its input, to create a framework
-to statically provide assurance that there is a certain limit on how much
+way that it is not feasible to recover the original contents (within the context
+of a certain threat model). An example is a hash function. This could be a
+mechanism to go from a secret variable to a public variable. The type system and
+analysis tool could then be modified to account for this. Perhaps it is also
+possible to allow the programmer to create new obfuscate functions, maybe using
+a restricted subset of the language. Also, it might be possible to use
+information theory concepts, like the conditional entropy~\cite{InfoTheory} of
+the function output conditioned on its input, to create a framework to
+statically provide assurance that there is a certain limit on how much
 information could be theoretically recovered (in general) after such a
-programmer-defined obfuscate function is applied.
+programmer-defined obfuscate function is applied. Perhaps a sub-language for
+obfuscate functions could be developed, which allows the expression of such
+``information losing'' functions, where a notion of ``information loss'' can
+be given by the programmers so that it fits the particular threat model
+that they are operating under. Then the implementation of the obfuscate
+functions could be statically checked to ensure that they do, in fact,
+follow this information loss specification. This might be able to be accomplished
+via an extension of the type system, similarly to how the type system is used in~\cite{Lifty}.
 

### 2020-12-11 paper/main.tex
wibble

@@
   A Spectre mitigation strategy in the form of a mechanism for marking variables
-  as ``non-speculative'' was developed in \cite{SpectreGuard}. In this paper, we
+  as ``non-speculative'' was developed in the form of \textit{SpectreGuard}\cite{SpectreGuard}. In this paper, we
   develop an embedded domain specific language (EDSL) in Haskell to provide
@@
 SpectreGuard is provides an abstraction that allows programmers to prevent
-speculative access of certain variables.~\cite{SpectreGuard} As Spectre-based
+speculative access of certain variables~\cite{SpectreGuard}. As Spectre-based
 attacks remain an issue, even in modern computer systems, such mitigations and
@@
 Haskell is a purely functional programming language with strong static type
-system based on System F and algebraic datatypes (ADTs).~\cite{HistoryOfHaskell}
+system based on System F and algebraic datatypes (ADTs)~\cite{HistoryOfHaskell}.
 These features, particularly the type system, the algebraic datatypes and its
@@
 straightforwardly expressed using ADTs using a \textit{deep
-embedding}.~\cite{DeepAndShallow}
+embedding}~\cite{DeepAndShallow}.
 
@@
 This is accomplished by recovering the type-level sensitivity type information at
-runtime. Such a recovery is made possible by the use of singletons.~\cite{Singletons}
+runtime. Such a recovery is made possible by the use of singletons~\cite{Singletons}.
 \ttt{for} loops provide a particular example of where Haskell's support for higher-order function
@@
 code generator can generate SpectreGuard annotations where appropriate. These annotations can
-then be used by the SpectreGuard mitigation system.~\cite{SpectreGuard}
+then be used by the SpectreGuard mitigation system~\cite{SpectreGuard}.
 
@@
 technique for writing programs at a type-level, which will be executed at
-compile-time by the type checker.~\cite{CertProg, DepHaskSpec} A more
+compile-time by the type checker~\cite{CertProg, DepHaskSpec}. A more
 lightweight technique, which might be able to be applied to allow for more
 expressive policies to control of information flow within the type system, would
-be the ``ghosts of departed proofs'' design technique.~\cite{DepartedProofs}
+be the ``ghosts of departed proofs'' design technique~\cite{DepartedProofs}.
 
@@
 mechanism which automatically fixes some (or all) leaks. Such a system has precendent
-in the previously mentioned paper \textit{Liquid Information Flow Control}.~\cite{Lifty}
+in the previously mentioned paper \textit{Liquid Information Flow Control}~\cite{Lifty}.
 This could give programmers an additional tool towards ensuring correctness, with
@@
 going the other direction could be provided by an instruction in the EDSL
-which might perform a Spectre mitigation measure, such as a cache flushes at appropriate times.~\cite{PLtea-james}
+which might perform a Spectre mitigation measure, such as a cache flushes at appropriate times~\cite{PLtea-james}.
 
@@
 these features is described in the upcoming paper \textit{On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages}, by
-David Young, Mark Grebe and Andy Gill.~\cite{PatMatchingEDSL}
+David Young, Mark Grebe and Andy Gill~\cite{PatMatchingEDSL}.
 

### 2020-12-11 paper/main.tex
Some final preparations

@@
 
-  A Spectre mitigation strategy in the form of a mechanism for marking variables
+  A Spectre mitigation strategy which allows variables to be marked
   as ``non-speculative'' was developed in the form of \textit{SpectreGuard}\cite{SpectreGuard}. In this paper, we
@@
   support for this feature, with a backend that generates C code. The static
-  type system of Haskell is used so that many basic forms of copying secret
+  type system of Haskell is used so that basic forms of copying secret
   variables to public variables are disallowed. Additionally, a static analysis
@@
 \label{sec:Introduction}
-SpectreGuard is provides an abstraction that allows programmers to prevent
+SpectreGuard provides an abstraction that allows programmers to prevent
 speculative access of certain variables~\cite{SpectreGuard}. As Spectre-based
@@
 preventative measures are crucial to maintaining the security of software.  For
-preserving program correctness, static analyses are desirable to prevent
-programmers from accidentally successfully compiling code which copies a
+preserving program correctness with respect to SpectreGuard annotations, static analyses are desirable to prevent
+programmers from accidentally compiling code which copies a
 ``secret'' variable (a variable protected by SpectreGuard) to a ``public''
 variable (a variable with no such protection). To this end, two interrelated
-static analysis techniques are designed and implemented.
+static analysis techniques are designed and implemented: one within the Haskell type system and
+one outside the type system.
 
@@
   can be applied to EDSL code. The results from this analysis take the form
-  of a forest of multiway trees, providing information about these possible
+  of a forest of multiway trees, providing information to the programmer about these possible
   indirect leaks.
@@
 
-Haskell is a purely functional programming language with strong static type
+Haskell is a purely functional programming language with a strong static type
 system based on System F and algebraic datatypes (ADTs)~\cite{HistoryOfHaskell}.
@@
 EDSLs. Expressions, commands and programs (compound commands) can be
-straightforwardly expressed using ADTs using a \textit{deep
+straightforwardly expressed using ADTs to construct a \textit{deep
 embedding}~\cite{DeepAndShallow}.
 
-A deep embedding directly exposes its abstract syntax tree (AST) as a value.
-This allows EDSL programs to be easily manipulated and examined, such as for
+A deep embedding of an EDSL directly exposes its abstract syntax tree (AST) as a value.
+This allows EDSL programs to be easily manipulated and examined, such as for the purposes of
 interpretation, code generation and static analysis (the latter two we make use
@@
 \label{sec:Syntax}
-A correspondence between the syntax of the EDSL, which is inherited from
+A correspondence between the syntax of the EDSL, which is in part inherited from
 Haskell, and the C language is given in Fig. \ref{fig:Syntax}. In the right column, an
@@
 code generator performs a transformation from code in the syntax given in the
-left column of Fig.~\ref{fig:Syntax} to the right column of the figure. This is
+left column of Fig.~\ref{fig:Syntax} to the syntax in the right column of that figure. This
 transformation recursively applies itself when it reaches the parts marked with
 an overline in the right column of the figure. It is worth noting that, as a
-result of this technique, the names in the generated C code will not generally
+result of the name generation technique used, the names in the generated C code will not generally
 be the same as the names in the EDSL code.
@@
 is how the loop variable in \ttt{for} loops can be tagged as secret (if appropriate).
-This is accomplished by recovering the type-level sensitivity type information at
+This is accomplished by recovering the type-level sensitivity information at
 runtime. Such a recovery is made possible by the use of singletons~\cite{Singletons}.
-\ttt{for} loops provide a particular example of where Haskell's support for higher-order function
+\ttt{for} loops provide a particular example of where Haskell's support for higher-order functions
 can be used inside an EDSL to implement commands that involve the creation of
@@
 The Haskell type system is leveraged to perform a basic static consistency check
-of the sensitivities of variables, so that a variable does not get assigned to a
+of the sensitivities of variables, so that the contents of a variable does not get assigned to a
 variable of a different sensitivity. This is done by making the \verb|Expr| type
-constructor take a phantom type argument~\cite{Phantom}. The phantom type
-argument is the \textit{sensitivity type} of that expression.  The logical
+constructor take a phantom type argument~\cite{Phantom} representing the sensitivity level. The phantom type
+argument is the \textit{sensitivity level} of that expression.  The logical
 inference rules corresponding to this check are given in Fig.
 \ref{fig:SensTypes}. Note that the EDSL inherits the rest of Haskell's type
-system in addition to these rules. Only the aspects of the type system that is
-particularly relevant to the EDSL is reflected in the figure, often specialized
-to the particular scenario encountered in using sensitivity types in the EDSL.
+system in addition to these rules. Only the aspects of the type system that are
+particularly relevant to the EDSL are reflected in the figure, often specialized
+to the particular scenario encountered in using sensitivity levels in the EDSL.
 An introduction to this style of inference rule system, with many examples and
@@
 
-Observe that an two expressions with different sensitivity types cannot be
+Observe that an two expressions with different sensitivity levels cannot be
 combined into a larger compound expression. However, commands (represented by
@@
 commands can be combined, even if they involve expressions with different
-sensitivity types. This freedom in combining commands independently of
+sensitivity levels. This freedom in combining commands independently of
 sensitivity foreshadows the essence of the problem we will encounter in
 Section \ref{sec:Analysis}. For now, note that all control flow constructs are
-part of the command type (as opposed to the expression type).
+part of the command type, as opposed to the expression type.
 
-Singletons~\cite{Singletons} are used to preserve this type level at runtime, so that the
+Singletons~\cite{Singletons} are used to preserve this type level information about sensitivities at runtime, so that the
 code generator can generate SpectreGuard annotations where appropriate. These annotations can
@@
 
-In Fig. \ref{fig:SensTypes}, it is assumed that $\tau$ and $\sigma$ are given by the
+In Fig. \ref{fig:SensTypes}, it is assumed that $\tau$ and $\sigma$ are metavariables given by the
 following grammar:
@@
 \end{minipage}}
-  \caption{Typing rules for sensitivity types}
+  \caption{Typing rules for sensitivity levels}
 \label{fig:SensTypes}
@@
 
-A couple of simple examples illustrate the basic typing rules:
+We now give a couple of simple examples illustrate the basic typing rules.
 
@@
 
+\pagebreak
 \begin{lstlisting}[language=haskell]
@@
 \noindent \ttt{example2} fails to type check since \ttt{array1} and \ttt{array2} have
-different sensitivity annotations, while the type of the \ttt{(.=)} operation
-requires that both arguments have the same sensitivity annotation. This restriction can
+different sensitivity levels, while the type of the \ttt{(.=)} operation
+requires that both arguments have the same sensitivity level. This restriction can
 be seen in the typing rule for \ttt{(.=)} in Fig. \ref{fig:SensTypes}.
@@
 
-The next slightly more complex example exhibits an important limitation of this sensitivity type checking:
+The next slightly more complex example exhibits an important limitation of this sensitivity level checking:
 
@@
 result of information being indirectly leaked from the secret variable to the
-public variable via a control flow construct: in this case, the innermost \ttt{for} loop. Such an example has been studied from programming language perspective before; for instance
+public variable via a control flow construct: in this case, the innermost \ttt{for} loop. Such an example has been studied from programming language perspective in the
+context of computer security before, for instance
 in~\cite{InfoFlowAnalysis}.
@@
 
-In Section \ref{sec:Examples}, a significant limitation of the sensitivity type checking
+In Section \ref{sec:Examples}, a significant limitation of the sensitivity level type checking
 was outlined. In this section we address this limitation using a static analysis technique.
@@
 if and only if the left-hand name is a public variable declared in the corresponding
-scope and the right-hand name is a secret variable in a conditional within the scope.
+scope and the right-hand name is a secret variable in a conditional immediately within the scope.
 
@@
 Whenever a declaration is encountered in EDSL code, the corresponding variable
-name is added to the scope stack with \ttt{scopeAddName}. Whenever a control
+name is added to the scope stack frame with \ttt{scopeAddName}. Whenever a control
 structure is entered (such as a \ttt{for} loop or an \ttt{if} statement),
@@
 type system, these invariants are machine-verified at compile-time.  Not only
-can these policy violations be detected, the system they develop is also able to
-fix leaks.
+can policy violations be detected and reported, the system they develop is also able to
+fix leaks automatically.
 
@@
 pure expression language separated from a command language, can be found in
-Winskel's 1993 book in the form of the \textbf{IMP} language.~\cite{WinskelBook} This
+Winskel's 1993 book in the form of the \textbf{IMP} language. This
 book provides an in-depth look at the three major mathematical formalizations
 of programming language semantics (axiomatic semantics, operational semantics and
-denotational semantics) and uses them to analyze \textbf{IMP}.
+denotational semantics) and uses them to analyze \textbf{IMP}.~\cite{WinskelBook}
 
@@
 expressive policies to control of information flow within the type system, would
-be the ``ghosts of departed proofs'' design technique~\cite{DepartedProofs}.
+be the ``ghosts of departed proofs'' design technique~\cite{DepartedProofs}. Another
+way to expand the expressiveness of the type system is through the use of \textit{refinement
+types}~\cite{RefinementTypes}, which have a Haskell implementation in the form of Liquid Haskell~\cite{LiquidHaskell}.
+Refinement types allow types which are given by restricting existing types using a predicate that
+the values of the type must satisfy. The predicate is written as a statement in
+a decidable logical framework.
 
@@
 mechanism which automatically fixes some (or all) leaks. Such a system has precendent
-in the previously mentioned paper \textit{Liquid Information Flow Control}~\cite{Lifty}.
+in the previously mentioned paper \textit{Liquid Information Flow Control}. This work uses refinement types, of the sort mentioned previously.~\cite{Lifty}
 This could give programmers an additional tool towards ensuring correctness, with
@@
 Other possible leak paths should also be investigated. While outside the scope of this paper,
-it there could be leaks which occur under circumstances other than direct copies or the indirect
+there could be leaks which occur under circumstances other than direct copies or the indirect
 leaks described in Section~\ref{sec:Analysis}. In future work, it would be useful to either
 classify more leak paths (and deal with them appropriately) or prove that, in fact, no such additional
-leak paths exist (at least, within a certain threat model).
+leak paths exist (within a certain threat model).
 
@@
 both direct copies from a secret variable to a public variable, as well as
-a certain class of leaks where control flow depends on a secret variable.
+a certain class of leaks that can occur when control flow depends on a secret variable.
 
